---
title: "ABCD_EnvVars_SEM"
author: "Wesley Meredith"
date: "11/26/2019"
output: pdf_document
---

```{r global_options, include = FALSE}

knitr::opts_chunk$set(message=FALSE, 
tidy.opts=list(width.cutoff=40), tidy = TRUE) 

```

```{r packages, include=FALSE, message=FALSE}

library(tidyverse)
library(lavaan)
library(semPlot)

data_dir_subs <- "/Users/wesleymeredith/Documents/data/0_data_output/enviro_factors/enviro_output/"

```

QUICK NOTE: I still need to implement the exploratory/confirmatory split in the data that we mentioned in the last meeting. These models are currently using all participants; will need to apply the site split

## Import z-scored environmental variables and "sociodemographic indicators

```{r import_data}

sem_cogdata <- read_csv(paste(data_dir_subs, 'allcogvars_zscore.csv', sep = ''))

sem_sociodem_vars <- colnames(sem_cogdata)[1:8]

sem_enviro_vars <- colnames(sem_cogdata)[9:47]

sem_cog_vars <- colnames(sem_cogdata)[48:ncol(sem_cogdata)]

```


## Specify model with all variables

```{r}

sem_enviro_model <- '
environment =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + FamSupport + IndepSelfReliance + Religion + 
FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance + SchoolEnvironment + SchoolInvolvement + SchoolDisengagement + 
NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + PM25Exposure + ProxRoads + ResDensity + CrimePC + ADI_Edu_LTHS + 
ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + ADI_IncDisparityIdx + ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + ADI_PercUnemp + ADI_PercFamPoverty + ADI_PercPovBelow128 + ADI_PercSingle + ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +     ADI_PercCrowding


sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

environment ~ a*sociodem 

cogfunc ~ b*environment + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

```


## Fit all variable model 

```{r}

sem_enviro_allvar <- sem(sem_enviro_model, sem_cogdata)

summary(sem_enviro_allvar, standardized = TRUE, fit.measures = TRUE)
```


## Rudimentary plot for SEM mediation with latent enviro variable from all ABCD measures

```{r}

pathfig_allvars <- semPaths(sem_enviro_allvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 1)

```


## Create SEM Model using Neighborhood, Home, School, and Culture latent variables for 4-way Environment mediation

```{r}

grouped_enviro_model <- '
neighborhood =~ NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + 
PM25Exposure + ProxRoads + ResDensity + CrimePC + ADI_Edu_LTHS + 
ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + ADI_IncDisparityIdx + 
ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + 
ADI_PercUnemp + ADI_PercFamPoverty + ADI_PercPovBelow128 + ADI_PercSingle + 
ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +   ADI_PercCrowding

home =~ FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance

school =~ SchoolEnvironment + SchoolInvolvement + SchoolDisengagement

culture =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + 
FamSupport + IndepSelfReliance + Religion

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + 
NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + WISC_Matrix + RAVLT_ShortDel + 
RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + 
Neuro_EmoRec + Neuro_StopSig + Neuro_MID

neighborhood ~ a1 * sociodem
home ~ a2 *sociodem
school ~ a3 * sociodem
culture ~ a4 * sociodem

cogfunc ~ c * sociodem

cogfunc ~ b1 * neighborhood
cogfunc ~ b2 * home
cogfunc ~ b3 * school
cogfunc ~ b4 * culture

neighborhood ~~ home
neighborhood ~~ school
neighborhood ~~ culture
home ~~ school
home ~~ culture
school ~~ culture

direct := c

indirect1 := a1*b1
indirect2 := a2*b2
indirect3 := a3*b3
indirect4 := a4*b4

contrast1 := indirect1 - indirect2
contrast2 := indirect1 - indirect3
contrast3 := indirect1 - indirect4
contrast4 := indirect2 - indirect3
contrast5 := indirect2 - indirect4
contrast6 := indirect3 - indirect4

total := c + (a1*b1) + (a2*b2) + (a3*b3) + (a4*b4)

'

```


## Fit 4-way mediation model

```{r}

sem_enviro_groupvar <- sem(grouped_enviro_model, sem_cogdata)

summary(sem_enviro_groupvar, standardized = TRUE, fit.measures = TRUE)

```


## Rudimentary plot for model with 4-way mediation using environment category lvs

```{r}

pathfig_groupvar <- semPaths(sem_enviro_groupvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Individual SEM models for each environmental factor category

```{r}

enviro_neigh_model <- '
neighborhood =~ NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + PM25Exposure + ProxRoads + ResDensity + CrimePC + ADI_Edu_LTHS + 
ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + ADI_IncDisparityIdx + ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + ADI_PercUnemp + ADI_PercFamPoverty + ADI_PercPovBelow128 + ADI_PercSingle + ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +   ADI_PercCrowding

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

neighborhood ~ a*sociodem 

cogfunc ~ b*neighborhood + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

enviro_home_model <- '
home =~ FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

home ~ a*sociodem 

cogfunc ~ b*home + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

enviro_school_model <- '
school =~ SchoolEnvironment + SchoolInvolvement + SchoolDisengagement

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

school ~ a*sociodem 

cogfunc ~ b*school + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

enviro_culture_model <- '
culture =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + FamSupport + IndepSelfReliance + Religion

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

culture ~ a*sociodem 

cogfunc ~ b*culture + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'
```


## Fits, visualizations, and summaries for individual models

```{r}

sem_enviro_neigh <- sem(enviro_neigh_model, sem_cogdata)

sem_enviro_home <- sem(enviro_home_model, sem_cogdata)

sem_enviro_school <- sem(enviro_school_model, sem_cogdata)

sem_enviro_cult <- sem(enviro_culture_model, sem_cogdata)


```
 

## Neighborhood figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_neigh, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## Home figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_home, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## School figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_school, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Culture figure

```{r}
pathfig_groupvar <- semPaths(sem_enviro_cult, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Neighborhood model summary

```{r}
summary(sem_enviro_neigh, standardized = TRUE, fit.measures = TRUE)
```


## Home model summary

```{r}
summary(sem_enviro_home, standardized = TRUE, fit.measures = TRUE)
```


## School model summary

```{r}
summary(sem_enviro_school, standardized = TRUE, fit.measures = TRUE)
```


## Culture model summary

```{r}
summary(sem_enviro_cult, standardized = TRUE, fit.measures = TRUE)
```

