---
title: "ABCD_EnvVars_CanCorr"
author: "Wesley Meredith"
output: pdf_document
---


Import libraries 

```{r libraries, warning=FALSE, message=FALSE}
library(CCA)
library(mosaic)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(plyr)
library(RGCCA)
library(Hmisc)
library(reshape2)

#add functions for bootstrapping can corrs
source("/Users/wesleymeredith/Documents/github_repos/cancorr_bootstrap/bootstrap.r", echo = FALSE)
source("/Users/wesleymeredith/Documents/github_repos/cancorr_bootstrap/sgcca.bootstrap.r", echo = FALSE)
source("/Users/wesleymeredith/Documents/github_repos/cancorr_bootstrap/aci.rgcca.r", echo = FALSE)

# set directory
data_dir <- "/Users/wesleymeredith/Documents/data/ABCD_release_2.0/"
data_dir_subs <- "/Users/wesleymeredith/Documents/data/0_data_output/enviro_factors/enviro_output/"
```

## Import residuals for environment variables and all cog scores, add colors used for enviro categories

Note that further into the script, txt files from Release 1.1 and Release 2 are required. I am currently searching for a variable that indicates while release a participant's data were first available for to eliminate the need for importing a Release 1.1 file.


```{r import_vars, message = FALSE, warning = FALSE}

allcog_vars <- read_csv(paste(data_dir_subs, 'ABCD_EnvVars_allcog.csv', sep = '')) %>%
  select(-Other)

color_teal <- "#77AAAD"
color_grey <- "#6E7783"
color_red <-  "#D7191C"
color_orange <- "#d2a273"
color_green<- "#729c6c"
color_blue <- "#2B83BA"

```


Z score the residuals, separate the enviro variables and outcome variables 

```{r}

allcog_zscores <- data.frame(matrix(nrow = nrow(allcog_vars), ncol = ncol(allcog_vars)))


for (i in 1:ncol(allcog_vars)){
    tmp_zscore <- as.matrix(zscore(allcog_vars[[i]]))
    allcog_zscores[,i] <-  tmp_zscore
    
}


colnames(allcog_zscores) <- colnames(allcog_vars)

write_csv(allcog_zscores, paste(data_dir_subs, 'allcogvars_zscore.csv', sep = ''))

envirovars_zscore <- allcog_zscores[,1:47]

cogscores_zscore <- allcog_zscores[,48:ncol(allcog_zscores)]
```


## Conduct canonical correlation analysis 

Correlate variables within and between enviro vars and cog scores
```{r}

correl <- matcor(envirovars_zscore, cogscores_zscore)

img.matcor(correl, type = 2)

img.matcor(correl, type = 1)

```


# RGCCA Canonical correlation  
Because the bootstrapping is time consuming and I wanted to more quickly access the results over time for generating my own figures for slides, etc., I save out the results from each CCA and bootstrap. 

```{r}

A <- list(envirovars_zscore, cogscores_zscore)

C <- matrix(c(0, 1, 1, 0), 2, 2)

result.rgcca_cogvars = rgcca(A, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))


save(result.rgcca_cogvars, file = "allcogvar_cca.RData")


```

Dim 1 plot 

```{r}

rgcca_cogvars.bootstrap.dim1 = aci.rgcca(object = result.rgcca_cogvars,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1)

save(rgcca_cogvars.bootstrap.dim1, file = "allcogvar_cca_boot1.RData")

```

Dim 2 plot

```{r}

rgcca_cogvars.bootstrap.dim2 = aci.rgcca(object = result.rgcca_cogvars,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2)

save(rgcca_cogvars.bootstrap.dim2, file = "allcogvar_cca_boot2.RData")

```


Dim 3 plot

```{r}

rgcca_cogvars.bootstrap.dim3 = aci.rgcca(object = result.rgcca_cogvars,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3)

save(rgcca_cogvars.bootstrap.dim3, file = "allcogvar_cca_boot3.RData")

```


Dim 4 plot 

```{r}

rgcca_cogvars.bootstrap.dim4 = aci.rgcca(object = result.rgcca_cogvars,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4)

save(rgcca_cogvars.bootstrap.dim4, file = "allcogvar_cca_boot4.RData")

```


## Complete split half comparisons

Append subject ID and site ID data for making split half decisions and make the split half groups

Here a Release 1.1 and Release 2 txt file are required.

```{r}

full_casesubs <- read_csv(paste(data_dir_subs, 'final_subjectlist_allcog.csv', sep = ''))

SiteID       <- read.delim(paste(data_dir, 'abcd_lt01.txt', sep = ''), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1) %>%
  filter(eventname == "baseline_year_1_arm_1") %>%
  select(src_subject_id, site_id_l) %>%
  filter(src_subject_id %in% full_casesubs[[1]])

site_allcogzscores <- allcog_zscores %>%
  mutate(subject_id = SiteID$src_subject_id,
         study_site = SiteID$site_id_l)

#Separate by a simple half-split
first_half_envirozscore <- envirovars_zscore[1:(floor(nrow(envirovars_zscore)/2)),] 
first_half_cogzscore <- cogscores_zscore[1:(floor(nrow(cogscores_zscore)/2)),]

last_half_envirozscore <- envirovars_zscore[(floor(nrow(envirovars_zscore)/2)+1): nrow(envirovars_zscore),]
last_half_cogzscore <- cogscores_zscore[(floor(nrow(cogscores_zscore)/2)+1): nrow(cogscores_zscore),]

#Separate first and second release participants

### This part may need to be rewritten since it's using a text file from the previous release (1.1) ###
first_release_subjects <- read.delim("/Users/wesleymeredith/Documents/data/ABCD1.1/acspsw02.txt", na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>%
  slice(-1) %>% 
  select(src_subject_id)

first_release_allcogzscores <- site_allcogzscores %>%
  filter(subject_id %in% first_release_subjects[[1]]) 

second_release_allcogzscores <- site_allcogzscores %>%
  filter(subject_id %nin% first_release_subjects[[1]]) 

first_release_envirozscores <- first_release_allcogzscores %>%
  select(1:47)

first_release_cogzscores <- first_release_allcogzscores %>%
  select(48:(ncol(first_release_allcogzscores)-2))

second_release_envirozscores <- second_release_allcogzscores %>%
  select(1:47)

second_release_cogzscores <- second_release_allcogzscores %>%
  select(48:(ncol(second_release_allcogzscores)-2))

#Separate out sites into two groups

studysite_list <- unique(site_allcogzscores$study_site)

firstsite_allcogzscores <- site_allcogzscores %>%
  filter(study_site %in% studysite_list[1:(length(studysite_list)/2)])

secondsite_allcogzscores <- site_allcogzscores %>%
  filter(study_site %in% studysite_list[((length(studysite_list)/2)+1):length(studysite_list)])

firstsite_envirozscores <- firstsite_allcogzscores %>%
  select(1:47)

firstsite_cogzscores <- firstsite_allcogzscores %>%
  select(48:(ncol(first_release_allcogzscores)-2))

secondsite_envirozscores <- secondsite_allcogzscores %>%
  select(1:47)

secondsite_cogzscores <- secondsite_allcogzscores %>%
  select(48:(ncol(second_release_allcogzscores)-2))

```

## Even half split

Even split first half CCA 
```{r}

A_firsthalf <- list(first_half_envirozscore, first_half_cogzscore)
A_secondhalf <- list(last_half_envirozscore, last_half_cogzscore)

C <- matrix(c(0, 1, 1, 0), 2, 2)

rgcca_firsthalf = rgcca(A_firsthalf, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))

save(rgcca_firsthalf, file = "allcogvar_cca_firsthalf.RData")

```

Even split first half dim 1 
```{r}
rgcca.bootstrap_firsthalf_dim1 = aci.rgcca(object = rgcca_firsthalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1)

save(rgcca.bootstrap_firsthalf_dim1, file = "allcogvar_cca_first_halfboot1.RData")
```


Even split first half dim 2 
```{r}
rgcca.bootstrap_firsthalf_dim2 = aci.rgcca(object = rgcca_firsthalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim  = 2)

save(rgcca.bootstrap_firsthalf_dim2, file = "allcogvar_cca_first_halfboot2.RData")
```

Even split first half dim 3
```{r}
rgcca.bootstrap_firsthalf_dim3 = aci.rgcca(object = rgcca_firsthalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim  = 3)

save(rgcca.bootstrap_firsthalf_dim3, file = "allcogvar_cca_first_halfboot3.RData")
```


Even split first half dim 4 
```{r}
rgcca.bootstrap_firsthalf_dim4 = aci.rgcca(object = rgcca_firsthalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim  = 4)

save(rgcca.bootstrap_firsthalf_dim4, file = "allcogvar_cca_first_halfboot4.RData")
```


## Even split second half CCA
```{r}

rgcca_secondhalf = rgcca(A_secondhalf, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))


```

Even split second half dim 1 
```{r}
rgcca.bootstrap_secondhalf_dim1 = aci.rgcca(object = rgcca_secondhalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1)

save(rgcca.bootstrap_secondhalf_dim1, file = "allcogvar_cca_second_halfboot1.RData")
```

Even split second half Dim 2 
```{r}
rgcca.bootstrap_secondhalf_dim2 = aci.rgcca(object = rgcca_secondhalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2)

save(rgcca.bootstrap_secondhalf_dim2, file = "allcogvar_cca_second_halfboot2.RData")
```


Even split second half Dim 3
```{r}

rgcca.bootstrap_secondhalf_dim3 = aci.rgcca(object = rgcca_secondhalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3)

save(rgcca.bootstrap_secondhalf_dim3, file = "allcogvar_cca_second_halfboot3.RData")

```

Even split second half Dim 4
```{r}
rgcca.bootstrap_secondhalf_dim4 = aci.rgcca(object = rgcca_secondhalf,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4,
          nb_cores = 3)

save(rgcca.bootstrap_secondhalf_dim4, file = "allcogvar_cca_second_halfboot4.RData")
```


## Comparing even split first and second half
```{r}

(evensplit_cor_dim1 <- cor.test(rgcca_firsthalf$a[[1]][,1], rgcca_secondhalf$a[[1]][,1], method = "spearman"))

(evensplit_cor_dim2 <- cor.test(rgcca_firsthalf$a[[1]][,2], rgcca_secondhalf$a[[1]][,2], method = "spearman"))

(evensplit_cor_dim3 <- cor.test(rgcca_firsthalf$a[[1]][,3], rgcca_secondhalf$a[[1]][,3], method = "spearman"))

(evensplit_cor_dim4 <- cor.test(rgcca_firsthalf$a[[1]][,4], rgcca_secondhalf$a[[1]][,4], method = "spearman"))

```


## First and Second release split

first release CCA 
```{r}

A_firstrelease <- list(first_release_envirozscores, first_release_cogzscores)
A_secondrelease <- list(second_release_envirozscores, second_release_cogzscores)

C <- matrix(c(0, 1, 1, 0), 2, 2)

rgcca_firstrel = rgcca(A_firstrelease, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))

save(rgcca_firstrel, file = "allcogvar_cca_firstrel.RData")

```

First release 1st dim
```{r}
rgcca.bootstrap_firstrel_boot1 = aci.rgcca(object = rgcca_firstrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1,
          nb_cores = 4)

save(rgcca.bootstrap_firstrel_boot1, file = "allcogvar_cca_firstrel_boot1.RData")


```

First release 2nd dim 
```{r}

rgcca.bootstrap_firstrel_boot2 = aci.rgcca(object = rgcca_firstrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2,
          nb_cores = 4)

save(rgcca.bootstrap_firstrel_boot2, file = "allcogvar_cca_firstrel_boot2.RData")

```

First release 3rd dim 
```{r}

rgcca.bootstrap_firstrel_boot3 = aci.rgcca(object = rgcca_firstrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3,
          nb_cores = 4)

save(rgcca.bootstrap_firstrel_boot3, file = "allcogvar_cca_firstrel_boot3.RData")

```


First release 4th dim 
```{r}

rgcca.bootstrap_firstrel_boot4 = aci.rgcca(object = rgcca_firstrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4,
          nb_cores = 4)

save(rgcca.bootstrap_firstrel_boot4, file = "allcogvar_cca_firstrel_boot4.RData")

```


## Second elease CCA 
```{r}

rgcca_secondrel = rgcca(A_secondrelease, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))

save(rgcca_secondrel, file = "allcogvar_cca_secondrel.RData")

```

Second release dim 1
```{r}

rgcca.bootstrap_secondrel_boot1 = aci.rgcca(object = rgcca_secondrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1,
          nb_cores = 4)

save(rgcca.bootstrap_secondrel_boot1, file = "allcogvar_cca_secondrel_boot1.RData")

```

Second release, dim 2 
```{r}

rgcca.bootstrap_secondrel_boot2 = aci.rgcca(object = rgcca_secondrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2,
          nb_cores = 4)

save(rgcca.bootstrap_secondrel_boot2, file = "allcogvar_cca_secondrel_boot2.RData")

```


Second release, dim 3
```{r}

rgcca.bootstrap_secondrel_boot3 = aci.rgcca(object = rgcca_secondrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3,
          nb_cores = 4)

save(rgcca.bootstrap_secondrel_boot3, file = "allcogvar_cca_secondrel_boot3.RData")

```

Second release, dim 4
```{r}

rgcca.bootstrap_secondrel_boot4 = aci.rgcca(object = rgcca_secondrel,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4,
          nb_cores = 4)

save(rgcca.bootstrap_secondrel_boot4, file = "allcogvar_cca_secondrel_boot4.RData")

```

## Compare first and second release split
```{r}

(releasesplit_cor_dim1 <- cor.test(rgcca_firstrel$a[[1]][,1], rgcca_secondrel$a[[1]][,1], mtehod = "spearman"))

(releasesplit_cor_dim2 <- cor.test(rgcca_firstrel$a[[1]][,2], rgcca_secondrel$a[[1]][,2], mtehod = "spearman"))

(releasesplit_cor_dim3 <- cor.test(rgcca_firstrel$a[[1]][,3], rgcca_secondrel$a[[1]][,3], mtehod = "spearman"))

(releasesplit_cor_dim4 <- cor.test(rgcca_firstrel$a[[1]][,4], rgcca_secondrel$a[[1]][,4], mtehod = "spearman"))

```


# Site splot, random
Moving forward, will need to seed a series of random combinations of the sites for split comparisons

Because the site numbers aren't in chronological order, for my first pass at site splitting, I just used the order of occurrence for each unique site numbering to split down the middle.

First site split CCA
```{r}

A_firstsite <- list(firstsite_envirozscores, firstsite_cogzscores)
A_secondsite <- list(secondsite_envirozscores, secondsite_cogzscores)

C <- matrix(c(0, 1, 1, 0), 2, 2)

rgcca_firstsite = rgcca(A_firstsite, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))

save(rgcca_firstsite, file = "allcogvar_cca_firstsite.RData")

```

First site split dim 1 

```{r}

rgcca.bootstrap_firstsite_boot1 = aci.rgcca(object = rgcca_firstsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1,
          nb_cores = 4)

save(rgcca.bootstrap_firstsite_boot1, file = "allcogvar_cca_firstsite_boot1.RData")

```

First site split dim 2

```{r}

rgcca.bootstrap_firstsite_boot2 = aci.rgcca(object = rgcca_firstsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2,
          nb_cores = 4)

save(rgcca.bootstrap_firstsite_boot2, file = "allcogvar_cca_firstsite_boot2.RData")

```

First site split dim 3

```{r}

rgcca.bootstrap_firstsite_boot3 = aci.rgcca(object = rgcca_firstsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3,
          nb_cores = 4)

save(rgcca.bootstrap_firstsite_boot3, file = "allcogvar_cca_firstsite_boot3.RData")

```

First site split dim 4

```{r}

rgcca.bootstrap_firstsite_boot4 = aci.rgcca(object = rgcca_firstsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4,
          nb_cores = 4)

save(rgcca.bootstrap_firstsite_boot4, file = "allcogvar_cca_firstsite_boot4.RData")

```


Second site split CCA
```{r}

rgcca_secondsite = rgcca(A_secondsite, C, tau = c(1, 1), scheme = "factorial", scale = TRUE,verbose = F, ncom = rep(10, length(A)))

save(rgcca_secondsite, file = "allcogvar_cca_secondsite.RData")

```

Second split dim 1

```{r}

rgcca.bootstrap_secondsite_boot1 = aci.rgcca(object = rgcca_secondsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 1,
          nb_cores = 4)

save(rgcca.bootstrap_secondsite_boot1, file = "allcogvar_cca_secondsite_boot1.RData")

```

Second split dim 2

```{r}

rgcca.bootstrap_secondsite_boot2 = aci.rgcca(object = rgcca_secondsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 2,
          nb_cores = 4)

save(rgcca.bootstrap_secondsite_boot2, file = "allcogvar_cca_secondsite_boot2.RData")

```

Second split dim 3

```{r}

rgcca.bootstrap_secondsite_boot3 = aci.rgcca(object = rgcca_secondsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 3,
          nb_cores = 4)

save(rgcca.bootstrap_secondsite_boot3, file = "allcogvar_cca_secondsite_boot3.RData")

```

Second split dim 4

```{r}

rgcca.bootstrap_secondsite_boot4 = aci.rgcca(object = rgcca_secondsite,
          A = A,
          B = 10000,
          alpha = 0.05,
          plot = "all",
          ndim = 4,
          nb_cores = 4)

save(rgcca.bootstrap_secondsite_boot4, file = "allcogvar_cca_secondsite_boot4.RData")

```


## Compare site splits 

```{r}

(sitesplit_cor_dim1 <- cor.test(rgcca_firstsite$a[[1]][,1], rgcca_secondsite$a[[1]][,1], method = "spearman"))

(sitesplit_cor_dim2 <- cor.test(rgcca_firstsite$a[[1]][,2], rgcca_secondsite$a[[1]][,2], method = "spearman"))

(sitesplit_cor_dim3 <- cor.test(rgcca_firstsite$a[[1]][,3], rgcca_secondsite$a[[1]][,3], method = "spearman"))

(sitesplit_cor_dim4 <- cor.test(rgcca_firstsite$a[[1]][,4], rgcca_secondsite$a[[1]][,4], method = "spearman"))

firstsite_allweight <- melt(rgcca_firstsite$a[[1]], id.vars = 1:2) %>%
  filter(Var2 %in% c(1:2)) %>%
  select(value)

secondsite_allweight <- melt(rgcca_secondsite$a[[1]], id.vars = 1:2) %>%
  filter(Var2 %in% c(1:2)) %>%
  select(value)

(sitesplit_cor_alldim <- cor.test(firstsite_allweight[[1]], secondsite_allweight[[1]], method = "spearman"))

```

## Gather data for creating personal CCA plots

For speed, I duplicated this code to generate the plots from individual data frames (many of which just overwrite the new data frame variable for the previous plot). When I circle back, I plan to gather all the results across dimensions using gather/spread to create columns for dimension and variable type so these plots can be generated more easily by filtering for the desired dimension

```{r}

combined_envirovar_list <- read_csv(paste(data_dir_subs, 'ABCD_EnvVars_combinedlist.csv', sep = ''))

fullcca_enviro <- data.frame(Weight =result.rgcca_cogvars$a[[1]][,1], Variable = rownames(result.rgcca_cogvars$a[[1]]))
rownames(fullcca_enviro) <- c()

## merge weight columns

fullcca_enviro_CI <- data.frame(rgcca_cogvars.bootstrap.dim1$CI[[1]][,2:3],
                                Variable = rownames(rgcca_cogvars.bootstrap.dim1$CI[[1]]))
rownames(fullcca_enviro_CI) <- c()

fullcca_enviro <- left_join(fullcca_enviro, fullcca_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
fullcca_enviro$Category[1:8] <- "Demo"

fullcca_enviro$Category <- factor(fullcca_enviro$Category)

### This commented section is preliminary work gathering all the results into a single data frame for easier use visualizing by filtering

# fullcca_enviro <- fullcca_enviro %>%
#   gather(Weight.1, Weight.2, Weight.3, Weight.4, key = "Dimension", value = "weight") %>%
#   gather(Dim1.Lower.Bound,Dim2.Lower.Bound, Dim3.Lower.Bound, Dim4.Lower.Bound, key = "lower_dim", value = "lower_CI") %>%
#   gather(Dim1.Upper.Bound, Dim2.Upper.Bound, Dim3.Upper.Bound, Dim4.Upper.Bound, key = "upper_dim", value = "upper_CI")

###

## Cog Vars

fullcca_cog <- data.frame(Weight =result.rgcca_cogvars$a[[2]][,1], Variable = rownames(result.rgcca_cogvars$a[[2]]))
rownames(fullcca_cog) <- c()

fullcca_cog_CI <- data.frame(rgcca_cogvars.bootstrap.dim1$CI[[2]][,2:3], Variable = rownames(rgcca_cogvars.bootstrap.dim1$CI[[2]]))
rownames(fullcca_cog_CI) <- c()

# fullcca_cog <- left_join(fullcca_cog, fullcca_cog_CI, by = "Variable") %>%
#       mutate(Variable = factor(Variable, levels = c("Neuro_StopSig", "Neuro_MID", "Neuro_EmoRec", "Neuro_0back", "Neuro_2back",
#                                                   "WISC_Matrix", "RAVLT_ShortDel", "RAVLT_LongDel", "CashChoice", "LittleMan","NIH_Reading",
#                                                   "NIH_PicVocab", "NIH_PicSeqMem", "NIH_PatternComp", "NIH_ListSorting_Scores",
#                                                   "NIH_Flanker", "NIH_CardSort")),
#            Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
#                     "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
#   mutate(Type = factor(Type))

fullcca_cog <- left_join(fullcca_cog, fullcca_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

```

## Plotting personal CCA cog and enviro figs (all participants)

```{r}

(fullcca_enviro_fig <- ggplot(data = fullcca_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = fullcca_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = fullcca_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(fullcca_cog_fig <- ggplot(data = fullcca_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = fullcca_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = fullcca_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```

Dim 2 Plot 

```{r}

fullcca_enviro <- data.frame(Weight =result.rgcca_cogvars$a[[1]][,2], Variable = rownames(result.rgcca_cogvars$a[[1]]))
rownames(fullcca_enviro) <- c()

## merge weight columns

fullcca_enviro_CI <- data.frame(rgcca_cogvars.bootstrap.dim2$CI[[1]][,2:3],
                                Variable = rownames(rgcca_cogvars.bootstrap.dim2$CI[[1]]))
rownames(fullcca_enviro_CI) <- c()

fullcca_enviro <- left_join(fullcca_enviro, fullcca_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
fullcca_enviro$Category[1:8] <- "Demo"

fullcca_enviro$Category <- factor(fullcca_enviro$Category)


## Cog Vars

fullcca_cog <- data.frame(Weight =result.rgcca_cogvars$a[[2]][,2], Variable = rownames(result.rgcca_cogvars$a[[2]]))
rownames(fullcca_cog) <- c()

fullcca_cog_CI <- data.frame(rgcca_cogvars.bootstrap.dim2$CI[[2]][,2:3], Variable = rownames(rgcca_cogvars.bootstrap.dim2$CI[[2]]))
rownames(fullcca_cog_CI) <- c()


fullcca_cog <- left_join(fullcca_cog, fullcca_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(fullcca_envirodim2_fig <- ggplot(data = fullcca_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = fullcca_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = fullcca_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(fullcca_cogdim2_fig <- ggplot(data = fullcca_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = fullcca_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = fullcca_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```

Dim 3 plot

```{r}

fullcca_enviro <- data.frame(Weight =result.rgcca_cogvars$a[[1]][,3], Variable = rownames(result.rgcca_cogvars$a[[1]]))
rownames(fullcca_enviro) <- c()

## merge weight columns

fullcca_enviro_CI <- data.frame(rgcca_cogvars.bootstrap.dim3$CI[[1]][,2:3],
                                Variable = rownames(rgcca_cogvars.bootstrap.dim3$CI[[1]]))
rownames(fullcca_enviro_CI) <- c()

fullcca_enviro <- left_join(fullcca_enviro, fullcca_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
fullcca_enviro$Category[1:8] <- "Demo"

fullcca_enviro$Category <- factor(fullcca_enviro$Category)


## Cog Vars

fullcca_cog <- data.frame(Weight =result.rgcca_cogvars$a[[2]][,3], Variable = rownames(result.rgcca_cogvars$a[[2]]))
rownames(fullcca_cog) <- c()

fullcca_cog_CI <- data.frame(rgcca_cogvars.bootstrap.dim3$CI[[2]][,2:3], Variable = rownames(rgcca_cogvars.bootstrap.dim3$CI[[2]]))
rownames(fullcca_cog_CI) <- c()


fullcca_cog <- left_join(fullcca_cog, fullcca_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(fullcca_envirodim3_fig <- ggplot(data = fullcca_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = fullcca_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = fullcca_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(fullcca_cogdim3_fig <- ggplot(data = fullcca_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = fullcca_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = fullcca_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```


## First Site Half Dim 1 

```{r}

sitefirsthalf_enviro <- data.frame(Weight =rgcca_firstsite$a[[1]][,1], Variable = rownames(rgcca_firstsite$a[[1]]))
rownames(sitefirsthalf_enviro) <- c()

## merge weight columns

sitefirsthalf_enviro_CI <- data.frame(rgcca.bootstrap_firstsite_boot1$CI[[1]][,2:3],
                                Variable = rownames(rgcca.bootstrap_firstsite_boot1$CI[[1]]))
rownames(sitefirsthalf_enviro_CI) <- c()

sitefirsthalf_enviro <- left_join(sitefirsthalf_enviro, sitefirsthalf_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
sitefirsthalf_enviro$Category[1:8] <- "Demo"

sitefirsthalf_enviro$Category <- factor(sitefirsthalf_enviro$Category)


## Cog Vars

sitefirsthalf_cog <- data.frame(Weight =rgcca_firstsite$a[[2]][,1], Variable = rownames(rgcca_firstsite$a[[2]]))
rownames(sitefirsthalf_cog) <- c()

sitefirsthalf_cog_CI <- data.frame(rgcca.bootstrap_firstsite_boot1$CI[[2]][,2:3], Variable = rownames(rgcca.bootstrap_firstsite_boot1$CI[[2]]))
rownames(sitefirsthalf_cog_CI) <- c()


sitefirsthalf_cog <- left_join(sitefirsthalf_cog, sitefirsthalf_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(sitefirsthalf_envirodim3_fig <- ggplot(data = sitefirsthalf_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = sitefirsthalf_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = sitefirsthalf_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(sitefirsthalf_cogdim3_fig <- ggplot(data = sitefirsthalf_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = sitefirsthalf_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = sitefirsthalf_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```

## First site split dim 2

```{r}

sitefirsthalf_enviro <- data.frame(Weight =rgcca_firstsite$a[[1]][,2], Variable = rownames(rgcca_firstsite$a[[1]]))
rownames(sitefirsthalf_enviro) <- c()

## merge weight columns

sitefirsthalf_enviro_CI <- data.frame(rgcca.bootstrap_firstsite_boot2$CI[[1]][,2:3],
                                Variable = rownames(rgcca.bootstrap_firstsite_boot2$CI[[1]]))
rownames(sitefirsthalf_enviro_CI) <- c()

sitefirsthalf_enviro <- left_join(sitefirsthalf_enviro, sitefirsthalf_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
sitefirsthalf_enviro$Category[1:8] <- "Demo"

sitefirsthalf_enviro$Category <- factor(sitefirsthalf_enviro$Category)


## Cog Vars

sitefirsthalf_cog <- data.frame(Weight =rgcca_firstsite$a[[2]][,2], Variable = rownames(rgcca_firstsite$a[[2]]))
rownames(sitefirsthalf_cog) <- c()

sitefirsthalf_cog_CI <- data.frame(rgcca.bootstrap_firstsite_boot2$CI[[2]][,2:3], Variable = rownames(rgcca.bootstrap_firstsite_boot2$CI[[2]]))
rownames(sitefirsthalf_cog_CI) <- c()


sitefirsthalf_cog <- left_join(sitefirsthalf_cog, sitefirsthalf_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(sitefirsthalf_envirodim3_fig <- ggplot(data = sitefirsthalf_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = sitefirsthalf_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = sitefirsthalf_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(sitefirsthalf_cogdim3_fig <- ggplot(data = sitefirsthalf_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = sitefirsthalf_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = sitefirsthalf_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```

## Second site split Dim 1

```{r}

sitesecondhalf_enviro <- data.frame(Weight =rgcca_secondsite$a[[1]][,1], Variable = rownames(rgcca_secondsite$a[[1]]))
rownames(sitesecondhalf_enviro) <- c()

## merge weight columns

sitesecondhalf_enviro_CI <- data.frame(rgcca.bootstrap_secondsite_boot1$CI[[1]][,2:3],
                                Variable = rownames(rgcca.bootstrap_secondsite_boot1$CI[[1]]))
rownames(sitesecondhalf_enviro_CI) <- c()

sitesecondhalf_enviro <- left_join(sitesecondhalf_enviro, sitesecondhalf_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
sitesecondhalf_enviro$Category[1:8] <- "Demo"

sitesecondhalf_enviro$Category <- factor(sitesecondhalf_enviro$Category)


## Cog Vars

sitesecondhalf_cog <- data.frame(Weight =rgcca_secondsite$a[[2]][,1], Variable = rownames(rgcca_secondsite$a[[2]]))
rownames(sitesecondhalf_cog) <- c()

sitesecondhalf_cog_CI <- data.frame(rgcca.bootstrap_secondsite_boot1$CI[[2]][,2:3], Variable = rownames(rgcca.bootstrap_secondsite_boot1$CI[[2]]))
rownames(sitesecondhalf_cog_CI) <- c()


sitesecondhalf_cog <- left_join(sitesecondhalf_cog, sitesecondhalf_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(sitesecondhalf_envirodim1_fig <- ggplot(data = sitesecondhalf_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = sitesecondhalf_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = sitesecondhalf_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(sitesecondhalf_cogdim1_fig <- ggplot(data = sitesecondhalf_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = sitesecondhalf_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = sitesecondhalf_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```



## Second site split Dim 2

```{r}

sitesecondhalf_enviro <- data.frame(Weight =rgcca_secondsite$a[[1]][,2], Variable = rownames(rgcca_secondsite$a[[1]]))
rownames(sitesecondhalf_enviro) <- c()

## merge weight columns

sitesecondhalf_enviro_CI <- data.frame(rgcca.bootstrap_secondsite_boot2$CI[[1]][,2:3],
                                Variable = rownames(rgcca.bootstrap_secondsite_boot2$CI[[1]]))
rownames(sitesecondhalf_enviro_CI) <- c()

sitesecondhalf_enviro <- left_join(sitesecondhalf_enviro, sitesecondhalf_enviro_CI, by = "Variable") %>%
  left_join(combined_envirovar_list, by = "Variable") 
  
sitesecondhalf_enviro$Category[1:8] <- "Demo"

sitesecondhalf_enviro$Category <- factor(sitesecondhalf_enviro$Category)


## Cog Vars

sitesecondhalf_cog <- data.frame(Weight =rgcca_secondsite$a[[2]][,2], Variable = rownames(rgcca_secondsite$a[[2]]))
rownames(sitesecondhalf_cog) <- c()

sitesecondhalf_cog_CI <- data.frame(rgcca.bootstrap_secondsite_boot2$CI[[2]][,2:3], Variable = rownames(rgcca.bootstrap_secondsite_boot2$CI[[2]]))
rownames(sitesecondhalf_cog_CI) <- c()


sitesecondhalf_cog <- left_join(sitesecondhalf_cog, sitesecondhalf_cog_CI, by = "Variable") %>%
      mutate(Type = c("NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NIH_tb", "NeuroCog", "NeuroCog", "NeuroCog", "NeuroCog",
                    "NeuroCog", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag", "NeuroImag")) %>%
  mutate(Type = factor(Type))

#Plot

(sitesecondhalf_envirodim2_fig <- ggplot(data = sitesecondhalf_enviro, aes(reorder(Variable, Variable), Weight)) +
  geom_bar(data = sitesecondhalf_enviro, aes(fill = Category),stat = "identity") +
  geom_errorbar(data = sitesecondhalf_enviro, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("Demo" = "gray", "Culture" = color_red, "Home" = color_orange, "Neighborhood" = color_green,
                                         "School" = color_blue)) +
  theme(axis.text.y = element_text(size = 7))
  

  
(sitesecondhalf_cogdim2_fig <- ggplot(data = sitesecondhalf_cog, aes(x = reorder(Variable, Variable), y = Weight)) +
  geom_bar(data = sitesecondhalf_cog, aes(fill = Type),stat = "identity") +
  geom_errorbar(data = sitesecondhalf_cog, mapping = aes(x = Variable, ymin = Lower.Bound, ymax = Upper.Bound)) +
  theme_classic() +
  coord_flip()) +
  scale_fill_manual("legend", values = c("NeuroCog" = "orange", "NeuroImag" = "thistle4", "NIH_tb" = "purple"))

```

