---
title: "ABCD_EnvVars_SEM"
author: "Wesley Meredith"
date: "11/26/2019"
output: pdf_document
---

```{r global_options, include = FALSE}

knitr::opts_chunk$set(message=FALSE, 
tidy.opts=list(width.cutoff=40), tidy = TRUE) 

```

```{r packages, include=FALSE, message=FALSE}

library(tidyverse)
library(lavaan)
library(semPlot)
library(FactoMineR)
library(factoextra)
library(magrittr)
library(FactoMineR)
library(mediation)
library(data.table)
library(corrplot)

data_dir_subs <- "/Users/wesleymeredith/Documents/data/0_data_output/enviro_factors/enviro_output/"

```

QUICK NOTE: I still need to implement the exploratory/confirmatory split in the data that we mentioned in the last meeting. These models are currently using all participants; will need to apply the site split

## Import z-scored environmental variables and "sociodemographic indicators

```{r import_data}

sem_cogdata <- read_csv(paste(data_dir_subs, 'allcogvars_zscore.csv', sep = ''))

#these aren't currently used, but wanted to be able to quickly label for any future visualizations if needed
sem_sociodem_vars <- colnames(sem_cogdata)[1:8]
sem_enviro_vars <- colnames(sem_cogdata)[9:52]
sem_cog_vars <- colnames(sem_cogdata)[53:ncol(sem_cogdata)]

```


## Create grouped variables each environment category: Home, School, Neighborhood, Culture. To be used for PCs in SEM models.

```{r}
#Culture Environment
CultureEnvVars_allcog <- sem_cogdata[,c("EthIdentExploration",
                                     "EthIdentCommitment",
                                     "FamObligation",
                                     "FamReferent",
                                     "FamSupport",
                                     "IndepSelfReliance",
                                     "Religion")]
#Home Envrionment 
HomeEnvVars_allcog <- sem_cogdata[,c("FamConflict_P",
                                     "ParentMonitoring",
                                     "FamConflict_Y",
                                     "ParentAcceptance")]
#School Environment
SchoolEnvVars_allcog <- sem_cogdata[,c("SchoolEnvironment",
                                       "SchoolInvolvement",
                                       "SchoolDisengagement")]
#Residential Environment
NeighborhoodEnvVars_allcog <- sem_cogdata[,c("NeighSafety_P",
                                             "NeighSafety_Y",
                                             "Walkability",
                                             "NO2Exposure",
                                             "PM25Exposure",
                                             "ProxRoads",
                                             "ResDensity",
                                             "UCR_ViolCrime_log", 
                                             "UCR_DrugAbuse_log", 
                                             "UCR_DrugSale_log", 
                                             "UCR_DrugPoss_log", 
                                             "UCR_DUI_log",  
                                             "UCR_MJSale_log",
                                             "ADI_Edu_LTHS",
                                             "ADI_Edu_HSDip",
                                             "ADI_Occ_WhiteCollar",
                                             "ADI_MedianFamInc",
                                             "ADI_IncDisparityIdx",
                                             "ADI_MedianHomeValue",
                                             "ADI_MedianGrossRent",
                                             "ADI_MedianMonthMortg",
                                             "ADI_PercHOwner",
                                             "ADI_PercUnemp",
                                             "ADI_PercFamPoverty",
                                             "ADI_PercPovBelow128",
                                             "ADI_PercSingle",
                                             "ADI_PercLogNCar",
                                             "ADI_PercLogNTel",
                                             "ADI_PercLogNPlumb",
                                             "ADI_PercCrowding")]
```

## Plot settings

```{r}
fig1_theme1 <- theme_minimal() + theme(legend.position="none", panel.grid.major = element_blank(), 
                                       panel.grid.minor = element_blank(), 
                                       axis.title.x = element_text(size = 14), 
                                       axis.title.y = element_text(colour = "black", size = 14),
                                       axis.text.x = element_text(size = 6),
                                       axis.text.y = element_text(size = 6))

fig1_theme2 <- theme_minimal() + theme(legend.position="none", panel.grid.major = element_blank(), 
                                       panel.grid.minor = element_blank(), 
                                       axis.title.x = element_text(size = 14), 
                                       axis.title.y = element_text(colour = "white", size = 14),
                                       axis.text.x = element_text(size = 6),
                                       axis.text.y = element_text(size = 6))

fig1_theme3 <- theme_minimal() + theme(legend.position="none", panel.grid.major = element_blank(), 
                                       panel.grid.minor = element_blank(),
                                       axis.title.x = element_text(colour = "white", size = 14), 
                                       axis.title.y = element_text(colour ="white", size = 14), 
                                       axis.text.x = element_text(colour="white"), 
                                       axis.text.y = element_text(colour="white"))

fig1_theme4 <- theme_minimal() + theme(legend.position="none", panel.grid.major = element_blank(), 
                                       panel.grid.minor = element_blank(), 
                                       axis.title.x = element_text(size = 14), 
                                       axis.title.y = element_text(colour = "white", size = 14),
                                       axis.text.x = element_text(size = 10),
                                       axis.text.y = element_blank())

color_teal <- "#77AAAD"
color_grey <- "#6E7783"
color_red <-  "#D7191C"
color_orange <- "#d2a273"
color_blue <- "#2B83BA"
color_green <- "#729c6c"

```


## Run PCA for each environment category. Append first PC from each category to dataframe.

```{r}

culture_pca     <- PCA(CultureEnvVars_allcog, scale.unit = TRUE, graph = FALSE)

home_pca        <- PCA(HomeEnvVars_allcog, scale.unit = TRUE, graph = FALSE)

school_pca      <- PCA(SchoolEnvVars_allcog, scale.unit = TRUE, graph = FALSE)

neighborhood_pca <- PCA(NeighborhoodEnvVars_allcog, scale.unit = TRUE, graph = FALSE)

allenviro_pca   <- PCA(sem_cogdata[9:52], scale.unit = TRUE, graph = FALSE)

sociodem_pca    <- PCA(sem_cogdata[1:8], scale.unit = TRUE, graph = FALSE)

cog_pca         <- PCA(sem_cogdata[53:69], scale.unit = TRUE, graph = FALSE)

sem_cogdata <- sem_cogdata %>%
        mutate(culture_PC1 = culture_pca$ind$coord[,1],
               home_PC1 = home_pca$ind$coord[,1],
               school_PC1 = school_pca$ind$coord[,1],
               neighborhood_PC1 = neighborhood_pca$ind$coord[,1],
               enviro_PC1 = allenviro_pca$ind$coord[,1],
               sociodem_PC1 = sociodem_pca$ind$coord[,1],
               cog_PC1 = cog_pca$ind$coord[,1])

```

## Plot the weights (and direction) of PC1 for environmental categories, sociodem variables, and cognitive scores

```{r}
## Culture 
culture_pccontrib <- data.table(Contribution = culture_pca$var$contrib[,1]) %>%
        mutate(Variable = rownames(culture_pca$var$contrib))

culture_pcdirect <- data.table(Coord = culture_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(culture_pca$var$coord))

negative_dir_culture <- which(culture_pcdirect$Coord < 0)
culture_pccontrib$Contribution[negative_dir_culture] <- -1 * culture_pccontrib$Contribution[negative_dir_culture]

(culture_pccontrib_plot <- culture_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_red) +
                coord_flip() +
                fig1_theme1 )

## Home 
home_pccontrib <- data.table(Contribution = home_pca$var$contrib[,1]) %>%
        mutate(Variable = rownames(home_pca$var$contrib))

home_pcdirect <- data.table(Coord = home_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(home_pca$var$coord))

negative_dir_home <- which(home_pcdirect$Coord < 0)
home_pccontrib$Contribution[negative_dir_home] <- -1 * home_pccontrib$Contribution[negative_dir_home]

(home_pccontrib_plot <- home_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_orange) +
                coord_flip() +
                fig1_theme1 )

## school 
school_pccontrib <- data.table(Contribution = school_pca$var$contrib[,1]) %>%
        mutate(Variable = rownames(school_pca$var$contrib))

school_pcdirect <- data.table(Coord = school_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(school_pca$var$coord))

negative_dir_school <- which(school_pcdirect$Coord < 0)
school_pccontrib$Contribution[negative_dir_school] <- -1 * school_pccontrib$Contribution[negative_dir_school]

(school_pccontrib_plot <- school_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_blue) +
                coord_flip() +
                fig1_theme1 )

## neighborhood
neighborhood_pccontrib <- data.table(Contribution = neighborhood_pca$var$contrib[,1])%>%
        mutate(Variable = rownames(neighborhood_pca$var$contrib))

neighborhood_pcdirect <- data.table(Coord = neighborhood_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(neighborhood_pca$var$coord))

negative_dir_neighborhood <- which(neighborhood_pcdirect$Coord < 0)
neighborhood_pccontrib$Contribution[negative_dir_neighborhood] <- -1 * neighborhood_pccontrib$Contribution[negative_dir_neighborhood]

(neighborhood_pccontrib_plot <- neighborhood_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_green) +
                coord_flip() +
                fig1_theme1 )

## sociodemographics
sociodem_pccontrib <- data.table(Contribution = sociodem_pca$var$contrib[,1]) %>%
        mutate(Variable = rownames(sociodem_pca$var$contrib))

sociodem_pcdirect <- data.table(Coord = sociodem_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(sociodem_pca$var$coord))

negative_dir_sociodem <- which(sociodem_pcdirect$Coord < 0)
sociodem_pccontrib$Contribution[negative_dir_sociodem] <- -1 * sociodem_pccontrib$Contribution[negative_dir_sociodem]

(sociodem_pccontrib_plot <- sociodem_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_grey) +
                coord_flip() +
                fig1_theme1 )

## cog scores 
cog_pccontrib <- data.table(Contribution = cog_pca$var$contrib[,1]) %>%
        mutate(Variable = rownames(cog_pca$var$contrib))

cog_pcdirect <- data.table(Coord = cog_pca$var$coord[,1]) %>%
        mutate(Variable = rownames(cog_pca$var$coord))

negative_dir_cog <- which(cog_pcdirect$Coord < 0)
cog_pccontrib$Contribution[negative_dir_cog] <- -1 * cog_pccontrib$Contribution[negative_dir_cog]

(cog_pccontrib_plot <- cog_pccontrib %>%
                ggplot(aes(x = reorder(Variable, Contribution), y = Contribution)) +
                geom_bar(stat = "identity", position = "dodge", fill = color_teal) +
                coord_flip() +
                fig1_theme1 )

```
## combine plots for all PC contributions

```{r}

(pc1_fullpop_combinedfig <- grid.arrange(culture_pccontrib_plot,
                                     home_pccontrib_plot,
                                     school_pccontrib_plot,
                                     neighborhood_pccontrib_plot,
                                     sociodem_pccontrib_plot,
                                     cog_pccontrib_plot,
                                     heights = c(1, 1, 1),
                                     nrow = 3))

ggsave('pc1_fullpop_combinedfig.png', pc1_fullpop_combinedfig, height = 13, width = 9)

```



# Correlations between variables (and PCs)

```{r}
variable_corr <- cor(sem_cogdata[,c(1:69)])
diag(variable_corr) <-  0
variable_corr_pvals <- sem_cogdata[,c(1:69)] %>%
        cor.mtest(method = "spearman")

variable_corrplot <- corrplot(variable_corr, method = 'color', type = "lower", diag = FALSE, p.mat =variable_corr_pvals$p, tl.cex = .5, tl.srt = 25, tl.col = "black",
                              insig = "label_sig", cl.pos = "b", pch.col = "black", pch.cex = .5, col = colorRampPalette(c("red", "white",
                                                                                                         "blue"))(200))

pc_corr <- cor(sem_cogdata[,c(70:75)])
diag(pc_corr) <- 0

pc_corr_pvals <- sem_cogdata[,c(70:75)] %>%
        cor.mtest(method = "spearman")

pc_corrplot <- corrplot(pc_corr, method = 'color', type = "lower", diag = FALSE, p.mat = pc_corr_pvals$p,
                              insig = "label_sig", cl.pos = "b", pch.col = "black", pch.cex = 2, outline = TRUE, addgrid.col = "gray", tl.col = "black", tl.srt = 25,
                        cl.lim = c(-0.7, 0.7), col = colorRampPalette(c("red","white", "blue"))(200))



```


# SEM models

## Specify model with all variables (singular environment LV from all variables)

```{r}

sem_enviro_model <- '
environment =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + FamSupport + IndepSelfReliance + Religion + 
FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance + SchoolEnvironment + SchoolInvolvement + SchoolDisengagement + 
NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + PM25Exposure + ProxRoads + ResDensity + UCR_ViolCrime_log + UCR_DrugAbuse_log + 
UCR_DrugSale_log + UCR_DrugPoss_log + UCR_DUI_log + UCR_MJSale_log + ADI_Edu_LTHS + ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + 
ADI_IncDisparityIdx + ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + ADI_PercUnemp + ADI_PercFamPoverty + 
ADI_PercPovBelow128 + ADI_PercSingle + ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +     ADI_PercCrowding


sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

environment ~ a*sociodem 

cogfunc ~ b*environment + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

```


## Fit all variable model 

```{r}

sem_enviro_allvar <- sem(sem_enviro_model, sem_cogdata)

summary(sem_enviro_allvar, standardized = TRUE, fit.measures = TRUE)
```


## Rudimentary plot for SEM mediation with latent enviro variable from all ABCD measures

```{r}

pathfig_allvars <- semPaths(sem_enviro_allvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 1)

```


## Create SEM Model using Neighborhood, Home, School, and Culture latent variables for 4-way Environment mediation

```{r}

grouped_enviro_model <- '
## specifying LVs individually for neigh, home, school, culture; sociodem; and cog
neighborhood =~ NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + 
PM25Exposure + ProxRoads + ResDensity + UCR_ViolCrime_log + UCR_DrugAbuse_log + UCR_DrugSale_log + 
UCR_DrugPoss_log + UCR_DUI_log + UCR_MJSale_log + ADI_Edu_LTHS + 
ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + ADI_IncDisparityIdx + 
ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + 
ADI_PercUnemp + ADI_PercFamPoverty + ADI_PercPovBelow128 + ADI_PercSingle + 
ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +   ADI_PercCrowding

home =~ FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance

school =~ SchoolEnvironment + SchoolInvolvement + SchoolDisengagement

culture =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + 
FamSupport + IndepSelfReliance + Religion

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + 
NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + WISC_Matrix + RAVLT_ShortDel + 
RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + 
Neuro_EmoRec + Neuro_StopSig + Neuro_MID

## setting up indirect paths (which includes the path labels) from sociodem 
neighborhood ~ a1 * sociodem
home ~ a2 *sociodem
school ~ a3 * sociodem
culture ~ a4 * sociodem

## setting up direct path from sociodem to cogfunc
cogfunc ~ c * sociodem

#setting up "direct" paths from enviro LVs to cogfunc
cogfunc ~ b1 * neighborhood
cogfunc ~ b2 * home
cogfunc ~ b3 * school
cogfunc ~ b4 * culture

## Measuring covariance between environmental factors
neighborhood ~~ home
neighborhood ~~ school
neighborhood ~~ culture
home ~~ school
home ~~ culture
school ~~ culture

## Pathways to analyze
# direct path (standard "C," from sociodem to cogfunc)
direct := c

# indirect pathways through each enviro factor
indirect1 := a1*b1
indirect2 := a2*b2
indirect3 := a3*b3
indirect4 := a4*b4

# total indirect, which adds each indirect effect 
tot_indirect := indirect1 + indirect2 + indirect3 + indirect4

# contrasted pathways, subtracting indirect paths from one another
contrast1 := indirect1 - indirect2
contrast2 := indirect1 - indirect3
contrast3 := indirect1 - indirect4
contrast4 := indirect2 - indirect3
contrast5 := indirect2 - indirect4
contrast6 := indirect3 - indirect4

#total path, accounting for direct sociodem to cogfunc and all indirect enviro factor paths
total := c + tot_indirect

'

```

## Fit 4-way mediation model

```{r}

sem_enviro_groupvar <- sem(grouped_enviro_model, sem_cogdata)

summary(sem_enviro_groupvar, standardized = TRUE, fit.measures = TRUE)

enviro_groupvar_params <- parameterEstimates(sem_enviro_groupvar, boot.ci.type = 'bca.simple')

```


## Rudimentary plot for model with 4-way mediation using environment category lvs

```{r}

pathfig_groupvar <- semPaths(sem_enviro_groupvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Similar 4-way SEM using 1st PC for each environmental category

```{r}

grouped_enviro_PCmodel <- '
## specifying LVs for sociodemographics and cognitive scores

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + 
NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + WISC_Matrix + RAVLT_ShortDel + 
RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + 
Neuro_EmoRec + Neuro_StopSig + Neuro_MID

## setting up indirect paths (which includes the path labels) from sociodem 
neighborhood_PC1 ~ a1 * sociodem
home_PC1 ~ a2 *sociodem
school_PC1 ~ a3 * sociodem
culture_PC1 ~ a4 * sociodem

## setting up direct path from sociodem to cogfunc
cogfunc ~ c * sociodem

#setting up "direct" paths from enviro LVs to cogfunc
cogfunc ~ b1 * neighborhood_PC1
cogfunc ~ b2 * home_PC1
cogfunc ~ b3 * school_PC1
cogfunc ~ b4 * culture_PC1

## Measuring covariance between environmental factors
neighborhood_PC1 ~~ home_PC1
neighborhood_PC1 ~~ school_PC1
neighborhood_PC1 ~~ culture_PC1
home_PC1 ~~ school_PC1
home_PC1 ~~ culture_PC1
school_PC1 ~~ culture_PC1

## Pathways to analyze
# direct path (standard "C," from sociodem to cogfunc)
direct := c

# indirect pathways through each enviro factor
indirect1 := a1*b1
indirect2 := a2*b2
indirect3 := a3*b3
indirect4 := a4*b4

# total indirect, which adds each indirect effect 
tot_indirect := indirect1 + indirect2 + indirect3 + indirect4

# contrasted pathways, subtracting indirect paths from one another
contrast1 := indirect1 - indirect2
contrast2 := indirect1 - indirect3
contrast3 := indirect1 - indirect4
contrast4 := indirect2 - indirect3
contrast5 := indirect2 - indirect4
contrast6 := indirect3 - indirect4

#total path, accounting for direct sociodem to cogfunc and all indirect enviro factor paths
total := c + tot_indirect

'

```

## Fit 4-way PC mediation model

```{r}

sem_enviro_groupPC <- sem(grouped_enviro_PCmodel, sem_cogdata)

summary(sem_enviro_groupPC, standardized = TRUE, fit.measures = TRUE)

enviro_groupPC_params <- parameterEstimates(sem_enviro_groupPC, boot.ci.type = 'bca.simple')

```



## Individual SEM models for each environmental factor category

```{r}

enviro_neigh_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

neighborhood_PC1 ~ a*sociodem 

cogfunc ~ b*neighborhood_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_home_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

home_PC1 ~ a*sociodem 

cogfunc ~ b*home_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_school_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

school_PC1 ~ a*sociodem 

cogfunc ~ b*school_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_culture_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

culture_PC1 ~ a*sociodem 

cogfunc ~ b*culture_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'
```


## Fits, visualizations, and summaries for individual models

```{r}

sem_enviro_neigh <- sem(enviro_neigh_model, sem_cogdata)

sem_enviro_home <- sem(enviro_home_model, sem_cogdata)

sem_enviro_school <- sem(enviro_school_model, sem_cogdata)

sem_enviro_cult <- sem(enviro_culture_model, sem_cogdata)


```
 

## Neighborhood figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_neigh, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## Home figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_home, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## School figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_school, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Culture figure

```{r}
pathfig_groupvar <- semPaths(sem_enviro_cult, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Neighborhood model summary

```{r}
summary(sem_enviro_neigh, standardized = TRUE, fit.measures = TRUE)
```


## Home model summary

```{r}
summary(sem_enviro_home, standardized = TRUE, fit.measures = TRUE)
```


## School model summary

```{r}

summary(sem_enviro_school, standardized = TRUE, fit.measures = TRUE)

```


## Culture model summary

```{r}

summary(sem_enviro_cult, standardized = TRUE, fit.measures = TRUE)

```

# Try mediation package 

## Culture mediation

```{r}

cult_totaleffect <- lm(cog_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(cult_totaleffect)

cult_demenviro_patha <- lm(culture_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(cult_demenviro_patha)

cult_envirocog_pathb <- lm(cog_PC1 ~ sociodem_PC1 + culture_PC1, data = sem_cogdata)
summary(cult_envirocog_pathb)


culture_mediation <- mediate(cult_demenviro_patha, cult_envirocog_pathb, treat = 'sociodem_PC1', mediator = 'culture_PC1',
                             boot = TRUE, sims = 1000, boot.ci.type = 'bca')

summary(culture_mediation)

```

## neighborhood mediation

```{r}

neigh_totaleffect <- lm(cog_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(neigh_totaleffect)

neigh_demenviro_patha <- lm(neighborhood_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(neigh_demenviro_patha)

neigh_envirocog_pathb <- lm(cog_PC1 ~ sociodem_PC1 + neighborhood_PC1, data = sem_cogdata)
summary(neigh_envirocog_pathb)


neigh_mediation <- mediate(neigh_demenviro_patha, neigh_envirocog_pathb, treat = 'sociodem_PC1', mediator = 'neighborhood_PC1',
                             boot = TRUE, sims = 1000, boot.ci.type = 'bca')

summary(neigh_mediation)

```

## school mediation 

```{r}


school_totaleffect <- lm(cog_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(school_totaleffect)

school_demenviro_patha <- lm(school_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(school_demenviro_patha)

school_envirocog_pathb <- lm(cog_PC1 ~ sociodem_PC1 + school_PC1, data = sem_cogdata)
summary(school_envirocog_pathb)


school_mediation <- mediate(school_demenviro_patha, school_envirocog_pathb, treat = 'sociodem_PC1', mediator = 'school_PC1',
                             boot = TRUE, sims = 1000, boot.ci.type = 'bca')

summary(school_mediation)

```

## home mediation

```{r}


home_totaleffect <- lm(cog_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(home_totaleffect)

home_demenviro_patha <- lm(home_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(home_demenviro_patha)

home_envirocog_pathb <- lm(cog_PC1 ~ sociodem_PC1 + home_PC1, data = sem_cogdata)
summary(home_envirocog_pathb)


home_mediation <- mediate(home_demenviro_patha, home_envirocog_pathb, treat = 'sociodem_PC1', mediator = 'home_PC1',
                             boot = TRUE, sims = 1000, boot.ci.type = 'bca')

summary(home_mediation)

```

## all enviro vars together 

```{r}

allenv_totaleffect <- lm(cog_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(allenv_totaleffect)

allenv_demenviro_patha <- lm(enviro_PC1 ~ sociodem_PC1, data = sem_cogdata)
summary(allenv_demenviro_patha)

allenv_envirocog_pathb <- lm(cog_PC1 ~ sociodem_PC1 + enviro_PC1, data = sem_cogdata)
summary(allenv_envirocog_pathb)


allenv_mediation <- mediate(allenv_demenviro_patha, allenv_envirocog_pathb, treat = 'sociodem_PC1', mediator = 'enviro_PC1',
                             boot = TRUE, sims = 10000, boot.ci.type = 'bca')

summary(allenv_mediation)

```

