---
title: "ABCD_EnvVars_SEM"
author: "Wesley Meredith"
date: "11/26/2019"
output: pdf_document
---

```{r global_options, include = FALSE}

knitr::opts_chunk$set(message=FALSE, 
tidy.opts=list(width.cutoff=40), tidy = TRUE) 

```

```{r packages, include=FALSE, message=FALSE}

library(tidyverse)
library(lavaan)
library(semPlot)
library(factoextra)
library(magrittr)
library(FactoMineR)

data_dir_subs <- "/Users/wesleymeredith/Documents/data/0_data_output/enviro_factors/enviro_output/"

```

QUICK NOTE: I still need to implement the exploratory/confirmatory split in the data that we mentioned in the last meeting. These models are currently using all participants; will need to apply the site split

## Import z-scored environmental variables and "sociodemographic indicators

```{r import_data}

sem_cogdata <- read_csv(paste(data_dir_subs, 'allcogvars_zscore.csv', sep = ''))

#these aren't currently used, but wanted to be able to quickly label for any future visualizations if needed
sem_sociodem_vars <- colnames(sem_cogdata)[1:8]
sem_enviro_vars <- colnames(sem_cogdata)[9:47]
sem_cog_vars <- colnames(sem_cogdata)[48:ncol(sem_cogdata)]

```


## Create grouped variables each environment category: Home, School, Neighborhood, Culture. To be used for PCs in SEM models.

```{r}
#Culture Environment
CultureEnvVars_allcog <- sem_cogdata[,c("EthIdentExploration",
                                     "EthIdentCommitment",
                                     "FamObligation",
                                     "FamReferent",
                                     "FamSupport",
                                     "IndepSelfReliance",
                                     "Religion")]
#Home Envrionment 
HomeEnvVars_allcog <- sem_cogdata[,c("FamConflict_P",
                                     "ParentMonitoring",
                                     "FamConflict_Y",
                                     "ParentAcceptance")]
#School Environment
SchoolEnvVars_allcog <- sem_cogdata[,c("SchoolEnvironment",
                                       "SchoolInvolvement",
                                       "SchoolDisengagement")]
#Residential Environment
NeighborhoodEnvVars_allcog <- sem_cogdata[,c("NeighSafety_P",
                                             "NeighSafety_Y",
                                             "Walkability",
                                             "NO2Exposure",
                                             "PM25Exposure",
                                             "ProxRoads",
                                             "ResDensity",
                                             "UCR_ViolCrime_log", 
                                             "UCR_DrugAbuse_log", 
                                             "UCR_DrugSale_log", 
                                             "UCR_DrugPoss_log", 
                                             "UCR_DUI_log",  
                                             "UCR_MJSale_log",
                                             "ADI_Edu_LTHS",
                                             "ADI_Edu_HSDip",
                                             "ADI_Occ_WhiteCollar",
                                             "ADI_MedianFamInc",
                                             "ADI_IncDisparityIdx",
                                             "ADI_MedianHomeValue",
                                             "ADI_MedianGrossRent",
                                             "ADI_MedianMonthMortg",
                                             "ADI_PercHOwner",
                                             "ADI_PercUnemp",
                                             "ADI_PercFamPoverty",
                                             "ADI_PercPovBelow128",
                                             "ADI_PercSingle",
                                             "ADI_PercLogNCar",
                                             "ADI_PercLogNTel",
                                             "ADI_PercLogNPlumb",
                                             "ADI_PercCrowding")]
```

## Run PCA for each environment category. Append first PC from each category to dataframe.

```{r}

culture_pca     <- PCA(CultureEnvVars_allcog, scale.unit = TRUE, graph = T)

home_pca        <- PCA(HomeEnvVars_allcog, scale.unit = TRUE, graph = T)

school_pca      <- PCA(SchoolEnvVars_allcog, scale.unit = TRUE, graph = T)

neighborhood_pca <- PCA(NeighborhoodEnvVars_allcog, scale.unit = TRUE, graph = T)

sem_cogdata <- sem_cogdata %>%
        mutate(culture_PC1 = culture_pca$ind$coord[,1],
               home_PC1 = home_pca$ind$coord[,1],
               school_PC1 = school_pca$ind$coord[,1],
               neighborhood_PC1 = neighborhood_pca$ind$coord[,1])

```



## Specify model with all variables (singular environment LV from all variables)

```{r}

sem_enviro_model <- '
environment =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + FamSupport + IndepSelfReliance + Religion + 
FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance + SchoolEnvironment + SchoolInvolvement + SchoolDisengagement + 
NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + PM25Exposure + ProxRoads + ResDensity + UCR_ViolCrime_log + UCR_DrugAbuse_log + 
UCR_DrugSale_log + UCR_DrugPoss_log + UCR_DUI_log + UCR_MJSale_log + ADI_Edu_LTHS + ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + 
ADI_IncDisparityIdx + ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + ADI_PercUnemp + ADI_PercFamPoverty + 
ADI_PercPovBelow128 + ADI_PercSingle + ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +     ADI_PercCrowding


sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

environment ~ a*sociodem 

cogfunc ~ b*environment + c*sociodem

indirect := a*b
direct := c
total := c + (a*b)

'

```


## Fit all variable model 

```{r}

sem_enviro_allvar <- sem(sem_enviro_model, sem_cogdata)

summary(sem_enviro_allvar, standardized = TRUE, fit.measures = TRUE)
```


## Rudimentary plot for SEM mediation with latent enviro variable from all ABCD measures

```{r}

pathfig_allvars <- semPaths(sem_enviro_allvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 1)

```


## Create SEM Model using Neighborhood, Home, School, and Culture latent variables for 4-way Environment mediation

```{r}

grouped_enviro_model <- '
## specifying LVs individually for neigh, home, school, culture; sociodem; and cog
neighborhood =~ NeighSafety_P + NeighSafety_Y + Walkability + NO2Exposure + 
PM25Exposure + ProxRoads + ResDensity + UCR_ViolCrime_log + UCR_DrugAbuse_log + UCR_DrugSale_log + 
UCR_DrugPoss_log + UCR_DUI_log + UCR_MJSale_log + ADI_Edu_LTHS + 
ADI_Edu_HSDip + ADI_Occ_WhiteCollar + ADI_MedianFamInc + ADI_IncDisparityIdx + 
ADI_MedianHomeValue + ADI_MedianGrossRent + ADI_MedianMonthMortg +   ADI_PercHOwner + 
ADI_PercUnemp + ADI_PercFamPoverty + ADI_PercPovBelow128 + ADI_PercSingle + 
ADI_PercLogNCar + ADI_PercLogNTel +ADI_PercLogNPlumb +   ADI_PercCrowding

home =~ FamConflict_P + ParentMonitoring + FamConflict_Y + ParentAcceptance

school =~ SchoolEnvironment + SchoolInvolvement + SchoolDisengagement

culture =~ EthIdentExploration + EthIdentCommitment + FamObligation + FamReferent + 
FamSupport + IndepSelfReliance + Religion

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + 
NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + WISC_Matrix + RAVLT_ShortDel + 
RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + 
Neuro_EmoRec + Neuro_StopSig + Neuro_MID

## setting up indirect paths (which includes the path labels) from sociodem 
neighborhood ~ a1 * sociodem
home ~ a2 *sociodem
school ~ a3 * sociodem
culture ~ a4 * sociodem

## setting up direct path from sociodem to cogfunc
cogfunc ~ c * sociodem

#setting up "direct" paths from enviro LVs to cogfunc
cogfunc ~ b1 * neighborhood
cogfunc ~ b2 * home
cogfunc ~ b3 * school
cogfunc ~ b4 * culture

## Measuring covariance between environmental factors
neighborhood ~~ home
neighborhood ~~ school
neighborhood ~~ culture
home ~~ school
home ~~ culture
school ~~ culture

## Pathways to analyze
# direct path (standard "C," from sociodem to cogfunc)
direct := c

# indirect pathways through each enviro factor
indirect1 := a1*b1
indirect2 := a2*b2
indirect3 := a3*b3
indirect4 := a4*b4

# total indirect, which adds each indirect effect 
tot_indirect := indirect1 + indirect2 + indirect3 + indirect4

# contrasted pathways, subtracting indirect paths from one another
contrast1 := indirect1 - indirect2
contrast2 := indirect1 - indirect3
contrast3 := indirect1 - indirect4
contrast4 := indirect2 - indirect3
contrast5 := indirect2 - indirect4
contrast6 := indirect3 - indirect4

#total path, accounting for direct sociodem to cogfunc and all indirect enviro factor paths
total := c + tot_indirect

'

```

## Fit 4-way mediation model

```{r}

sem_enviro_groupvar <- sem(grouped_enviro_model, sem_cogdata)

summary(sem_enviro_groupvar, standardized = TRUE, fit.measures = TRUE)

enviro_groupvar_params <- parameterEstimates(sem_enviro_groupvar, boot.ci.type = 'bca.simple')

```


## Rudimentary plot for model with 4-way mediation using environment category lvs

```{r}

pathfig_groupvar <- semPaths(sem_enviro_groupvar, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Similar 4-way SEM using 1st PC for each environmental category

```{r}

grouped_enviro_PCmodel <- '
## specifying LVs for sociodemographics and cognitive scores

sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + 
NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + WISC_Matrix + RAVLT_ShortDel + 
RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + 
Neuro_EmoRec + Neuro_StopSig + Neuro_MID

## setting up indirect paths (which includes the path labels) from sociodem 
neighborhood_PC1 ~ a1 * sociodem
home_PC1 ~ a2 *sociodem
school_PC1 ~ a3 * sociodem
culture_PC1 ~ a4 * sociodem

## setting up direct path from sociodem to cogfunc
cogfunc ~ c * sociodem

#setting up "direct" paths from enviro LVs to cogfunc
cogfunc ~ b1 * neighborhood_PC1
cogfunc ~ b2 * home_PC1
cogfunc ~ b3 * school_PC1
cogfunc ~ b4 * culture_PC1

## Measuring covariance between environmental factors
neighborhood_PC1 ~~ home_PC1
neighborhood_PC1 ~~ school_PC1
neighborhood_PC1 ~~ culture_PC1
home_PC1 ~~ school_PC1
home_PC1 ~~ culture_PC1
school_PC1 ~~ culture_PC1

## Pathways to analyze
# direct path (standard "C," from sociodem to cogfunc)
direct := c

# indirect pathways through each enviro factor
indirect1 := a1*b1
indirect2 := a2*b2
indirect3 := a3*b3
indirect4 := a4*b4

# total indirect, which adds each indirect effect 
tot_indirect := indirect1 + indirect2 + indirect3 + indirect4

# contrasted pathways, subtracting indirect paths from one another
contrast1 := indirect1 - indirect2
contrast2 := indirect1 - indirect3
contrast3 := indirect1 - indirect4
contrast4 := indirect2 - indirect3
contrast5 := indirect2 - indirect4
contrast6 := indirect3 - indirect4

#total path, accounting for direct sociodem to cogfunc and all indirect enviro factor paths
total := c + tot_indirect

'

```

## Fit 4-way PC mediation model

```{r}

sem_enviro_groupPC <- sem(grouped_enviro_PCmodel, sem_cogdata)

summary(sem_enviro_groupPC, standardized = TRUE, fit.measures = TRUE)

enviro_groupPC_params <- parameterEstimates(sem_enviro_groupPC, boot.ci.type = 'bca.simple')

```



## Individual SEM models for each environmental factor category

```{r}

enviro_neigh_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

neighborhood_PC1 ~ a*sociodem 

cogfunc ~ b*neighborhood_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_home_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

home_PC1 ~ a*sociodem 

cogfunc ~ b*home_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_school_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

school_PC1 ~ a*sociodem 

cogfunc ~ b*school_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'

enviro_culture_model <- '
sociodem =~ Age + Male + White + Black + Hispanic + Asian + Income + Education

cogfunc =~ NIH_ListSorting_Scores + NIH_PicVocab + NIH_Flanker + NIH_CardSort + NIH_PatternComp + NIH_PicSeqMem + NIH_Reading + 
WISC_Matrix + RAVLT_ShortDel + RAVLT_LongDel + LittleMan + CashChoice + Neuro_0back + Neuro_2back + Neuro_EmoRec + Neuro_StopSig + 
Neuro_MID

culture_PC1 ~ a*sociodem 

cogfunc ~ b*culture_PC1 + c*sociodem

indirect := a*b
direct := c
total := c + indirect

'
```


## Fits, visualizations, and summaries for individual models

```{r}

sem_enviro_neigh <- sem(enviro_neigh_model, sem_cogdata)

sem_enviro_home <- sem(enviro_home_model, sem_cogdata)

sem_enviro_school <- sem(enviro_school_model, sem_cogdata)

sem_enviro_cult <- sem(enviro_culture_model, sem_cogdata)


```
 

## Neighborhood figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_neigh, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## Home figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_home, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```
 
 
## School figure 

```{r}
pathfig_groupvar <- semPaths(sem_enviro_school, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Culture figure

```{r}
pathfig_groupvar <- semPaths(sem_enviro_cult, what = "stand", whatLabels = "stand", layout = "tree2", rotation = 4)

```


## Neighborhood model summary

```{r}
summary(sem_enviro_neigh, standardized = TRUE, fit.measures = TRUE)
```


## Home model summary

```{r}
summary(sem_enviro_home, standardized = TRUE, fit.measures = TRUE)
```


## School model summary

```{r}

summary(sem_enviro_school, standardized = TRUE, fit.measures = TRUE)

```


## Culture model summary

```{r}

summary(sem_enviro_cult, standardized = TRUE, fit.measures = TRUE)

```

