---
title: "ABCD Environment Variable Setup"
author: "Carlos Cardenas-Iniguez, Wesley Meredith"
date: "9/23/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = 'hide', message = F, warning = F)
```
## Setting up variables for PLS

This document outlines how I've gathered variables from ABCD Curated Release 2.0.1. The general flow of the document will be to pull all relevant variables from each instrument, and then filter for the various models. 

This script preps the data for use in all further analyses, including PCA, CCA, and SEM mediation models. 

NOTE: This script works off the full release txt files, NOT DEAP 

```{r libraries, echo = FALSE, results = 'hide'}

library(dplyr); library(ggplot2); library(lme4); library(cvTools);  library(R.matlab); library(summarytools); library(readr);
library(psych)
library(lme4)
library(stargazer)
library(gvlma)
library(extrafont)
library(lattice)
library(summarytools)
library(dplyr)
library(ade4)
library(factoextra)
library(magrittr)
library(FactoMineR)
library(tidyr)
library(fastDummies) #useful for dummy_cols command

# set directories for txt file locations and save location for csv
data_dir <- "/Users/wesleymeredith/Documents/data/ABCD_release_2.0/"
data_dir_subs <- "/Users/wesleymeredith/Documents/data/0_data_output/enviro_factors/enviro_output/"

```
In the following section, I will import the text file containing each variable, however, I am taking a two-step process, since the actual values do not begin until line 3. So: I first import the first line as the column names, and then combine that with the imported data using the `readr` package. 


## Demographic Variables

This first section imports demographic variables, such as race, ethnicity, gender, and age.

```{r Demographics, echo = FALSE, results= 'hide'}
acspsw03_n <-   sprintf('%s/acspsw03.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
acspsw03  <- sprintf('%s/acspsw03.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = acspsw03_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1")

acspsw03$race_ethnicity <- factor(acspsw03$race_ethnicity, levels = 1:5,
                                  labels = c("white", "black","hispanic","asian", "other"))

colnames(acspsw03)[8] <- "gender"
```


### Before filtering the demographic variables, create list for excluding family-excluded subset using FamilyID

In order to make sure that the nested structure of families does not contribute to the effects observed between environmental factors and working memory, a subset that has randomly excluded all family members besides one (if there are multiple) will be compared against the full sample. 

```{r FamilyExclusion, echo = FALSE}

family_idx <- data.frame()

for (i in acspsw03$rel_family_id) {
  tmp_ids <- (which(acspsw03$rel_family_id %in% i))
  
  family_idx <- rbind(tmp_ids[1], family_idx)
  rm(tmp_ids)

}

family_idx  <- unique(family_idx)
data.family <- acspsw03[family_idx$X1L, 5] #grab the src_family_id variable for the unique family members

```

### Now filter the demographic variables 

```{r DemographicVariablesIncluded}
acspsw03 <- acspsw03 %>% dummy_cols(ignore_na = TRUE, select_columns = c("race_ethnicity", "gender"))%>%
  select(src_subject_id, 
         interview_age,
         gender_M,
         gender_F,
         race_ethnicity_white,
         race_ethnicity_black,
         race_ethnicity_hispanic,
         race_ethnicity_asian,
         race_ethnicity_other,
         race_ethnicity,
         gender)

acspsw03_family <- acspsw03 %>%
  filter(src_subject_id %in% data.family[[1]])
```


## Socioeconomic Status Variables 

In this section I import socioeconomic status variables. Since the data are collected in categories, I used the data in the ABCD-STUDY git-hub to create the three bins for household income, and 5 bins for the education variable.

```{r SocioeconomicStatusVars, echo=FALSE}
pdem02_n <-   sprintf('%s/pdem02.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
pdem02  <- sprintf('%s/pdem02.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = pdem02_n, na = c('','NA'), guess_max = 11000) 

household.income = pdem02$demo_comb_income_v2
household.income[pdem02$demo_comb_income_v2 == "1"] = 1 #  Less than $5,000
household.income[pdem02$demo_comb_income_v2 == "2"] = 2 # $5,000 through $11,999
household.income[pdem02$demo_comb_income_v2 == "3"] = 3 # $12,000 through $15,999
household.income[pdem02$demo_comb_income_v2 == "4"] = 4 # $16,000 through $24,999
household.income[pdem02$demo_comb_income_v2 == "5"] = 5 # $25,000 through $34,999
household.income[pdem02$demo_comb_income_v2 == "6"] = 6 # $35,000 through $49,999
household.income[pdem02$demo_comb_income_v2 == "7"] = 7 # $50,000 through $74,999
household.income[pdem02$demo_comb_income_v2 == "8"] = 8 # $75,000 through $99,999
household.income[pdem02$demo_comb_income_v2 == "9"] = 9 # $100,000 through $199,999
household.income[pdem02$demo_comb_income_v2 == "10"] = 10 # $200,000 and greater
household.income[pdem02$demo_comb_income_v2 == "777"] = NA
household.income[pdem02$demo_comb_income_v2 == "999"] = NA
household.income[household.income %in% c(NA, "999", "777")] = NA
pdem02$household.income = factor( household.income, levels= 1:10, 
                                  labels = c("LT5K", "8.5K", "14K", "20.5K", "30K",
                                             "42.5K", "62.5K", "87.5K", "150K", "200KP") )

highest.education = rep("999", length(pdem02$demo_prnt_ed_v2b))
highest.education[pdem02$demo_prnt_ed_v2 == "0"] = 1
highest.education[pdem02$demo_prnt_ed_v2 == "1"] = 4
highest.education[pdem02$demo_prnt_ed_v2 == "2"] = 5
highest.education[pdem02$demo_prnt_ed_v2 == "3"] = 6
highest.education[pdem02$demo_prnt_ed_v2 == "4"] = 7
highest.education[pdem02$demo_prnt_ed_v2 == "5"] = 8
highest.education[pdem02$demo_prnt_ed_v2 == "6"] = 9
highest.education[pdem02$demo_prnt_ed_v2 == "7"] = 10
highest.education[pdem02$demo_prnt_ed_v2 == "8"] = 11
highest.education[pdem02$demo_prnt_ed_v2 == "9"] = 12
highest.education[pdem02$demo_prnt_ed_v2 == "10"] = 13
highest.education[pdem02$demo_prnt_ed_v2 == "11"] = 14
highest.education[(pdem02$demo_prnt_ed_v2 == "12") | (pdem02$demo_prnt_ed_v2 == "13")] = 16
highest.education[pdem02$demo_prnt_ed_v2 == "14"] = 17
highest.education[pdem02$demo_prnt_ed_v2 == "15"] = 18
highest.education[(pdem02$demo_prnt_ed_v2 == "16") | (pdem02$demo_prnt_ed_v2 == "17")] = 20
highest.education[pdem02$demo_prnt_ed_v2 == "18"] = 21
highest.education[pdem02$demo_prnt_ed_v2 == "19"] = 22
highest.education[pdem02$demo_prnt_ed_v2 == "20"] = 23
highest.education[pdem02$demo_prnt_ed_v2 == "21"] = 24
highest.education[pdem02$demo_prnt_ed_v2 == "777"] = 999
highest.education[highest.education == 999] = NA

highest.education2 = rep("999", length(pdem02$demo_prtnr_ed_v2))
highest.education2[pdem02$demo_prtnr_ed_v2 == "0"] = 1
highest.education2[pdem02$demo_prtnr_ed_v2 == "1"] = 4
highest.education2[pdem02$demo_prtnr_ed_v2 == "2"] = 5
highest.education2[pdem02$demo_prtnr_ed_v2 == "3"] = 6
highest.education2[pdem02$demo_prtnr_ed_v2 == "4"] = 7
highest.education2[pdem02$demo_prtnr_ed_v2 == "5"] = 8
highest.education2[pdem02$demo_prtnr_ed_v2 == "6"] = 9
highest.education2[pdem02$demo_prtnr_ed_v2 == "7"] = 10
highest.education2[pdem02$demo_prtnr_ed_v2 == "8"] = 11
highest.education2[pdem02$demo_prtnr_ed_v2 == "9"] = 12
highest.education2[pdem02$demo_prtnr_ed_v2 == "10"] = 13
highest.education2[pdem02$demo_prtnr_ed_v2 == "11"] = 14
highest.education2[(pdem02$demo_prtnr_ed_v2 == "12") | (pdem02$demo_prtnr_ed_v2 == "13")] = 16
highest.education2[pdem02$demo_prtnr_ed_v2 == "14"] = 17
highest.education2[pdem02$demo_prtnr_ed_v2 == "15"] = 18
highest.education2[(pdem02$demo_prtnr_ed_v2 == "16") | (pdem02$demo_prtnr_ed_v2 == "17")] = 20
highest.education2[pdem02$demo_prtnr_ed_v2 == "18"] = 21
highest.education2[pdem02$demo_prtnr_ed_v2 == "19"] = 22
highest.education2[pdem02$demo_prtnr_ed_v2 == "20"] = 23
highest.education2[pdem02$demo_prtnr_ed_v2 == "21"] = 24
highest.education2[pdem02$demo_prtnr_ed_v2 == "777"] = 999
highest.education2[highest.education2 == 999] = NA
pdem02$highest.education = factor( as.character(pmax(as.numeric(highest.education), as.numeric(highest.education2),na.rm=T)), levels=c(9,10,11,12,13,14,15,16,17,18,20,21,22,23,24), labels=c("9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "20", "21", "22", "23", "24") )

high.educ1 = pdem02$demo_prnt_ed_v2
high.educ2 = pdem02$demo_prtnr_ed_v2
high.educ1[which(high.educ1 == "999")] = NA
high.educ2[which(high.educ2 == "999")] = NA
high.educ1[which(high.educ1 == "777")] = NA
high.educ2[which(high.educ2 == "777")] = NA
high.educ = pmax(as.numeric(as.character(high.educ1)), as.numeric(as.character(high.educ2)), na.rm=T)
idx <- which(high.educ %in% 0:12, arr.ind = TRUE)
high.educ[idx] = 1 # "< HS Diploma"
idx <- which(high.educ %in% 13:14, arr.ind = TRUE)
high.educ[idx] = 2 # "HS Diploma/GED"
idx <- which(high.educ %in% 15:17, arr.ind = TRUE)
high.educ[idx] = 3 # "Some College"
idx <- which(high.educ == 18, arr.ind = TRUE)
high.educ[idx] = 4 # "Bachelor"
idx <- which(high.educ %in% 19:21, arr.ind = TRUE)
high.educ[idx] = 5 # "Post Graduate Degree"
high.educ[which(high.educ == "999")]=NA
high.educ[which(high.educ == "777")]=NA
pdem02$high.educ = factor( high.educ, levels= 1:5, labels = c("LTHSDiploma","HSDiplomaGED","SomeCollege","Bachelor","PostGradDegree") )

household.income_num <- paste(pdem02$household.income)
household.income_num[household.income_num == "LT5K"] = 5000 #  Less than $5,000
household.income_num[household.income_num == "8.5K"] = 8500 # $5,000 through $11,999
household.income_num[household.income_num == "14K"] = 14000 # $12,000 through $15,999
household.income_num[household.income_num == "20.5K"] = 20500 # $16,000 through $24,999
household.income_num[household.income_num == "30K"] = 30000 # $25,000 through $34,999
household.income_num[household.income_num == "42.5K"] = 42500 # $35,000 through $49,999
household.income_num[household.income_num == "62.5K"] = 62500 # $50,000 through $74,999
household.income_num[household.income_num == "87.5K"] = 87500 # $75,000 through $99,999
household.income_num[household.income_num == "150K"] = 150000 # $100,000 through $199,999
household.income_num[household.income_num == "200KP"] = 200000 # $200,000 and greater
pdem02$household.income_num <- as.numeric(household.income_num)

pdem02 <- pdem02 %>% 
    select(src_subject_id,
         highest.education,
         household.income_num)

```


## Parent-reported Family Culture and Home Environment 
The following section includes variables corresponding to family culture and family environment, as reported by parents. This includes the following measures: MACV, MEIM, Neighborhood Safety, Family Conflict, Prosocial Behavior.

```{r ParentReportVars, echo=TRUE}

sscep_n <-   sprintf('%s/abcd_sscep01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
sscep  <- sprintf('%s/abcd_sscep01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = sscep_n, na = c('','NA','999','777'), guess_max = 11000) %>%
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, #id
         meim_p_ss_exp,#meim exploration subscale
         meim_p_ss_com, # meim commitment & attachment subscale 
         nsc_p_ss_mean_3_items, #neighborhood safety mean
         fes_p_ss_fc_pr, #family environment scale: conflict (prorated based on num answered)
         macv_p_ss_fo, #Mexican Acculturation Values: family obligation
         macv_p_ss_fr, #Mexican Acculturation Values: family as referent
         macv_p_ss_fs, #Mexican Acculturation Values: family support
         macv_p_ss_isr, #Mexican Acculturation Values: ind. & self-reliance
         macv_p_ss_r #Mexican Acculturation Values: religion
         )

sscep_family <- sscep %>%
  filter(src_subject_id %in% data.family[[1]])
```


## Youth-reported School/Family Social Environment 
The following section includes variables corresponding to  family/school social environment, as reported by youth. This includes the following measures: School and Protective Factors Survey, Parental Monitoring, Family Conflict, Prosocial Behavior, Caregiver Acceptance, and Neighborhood Safety.

```{r YouthReportVars,echo=TRUE}

sscey_n <-   sprintf('%s/abcd_sscey01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
sscey  <- sprintf('%s/abcd_sscey01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = sscey_n, na = c('','NA','999','777'), guess_max = 11000) %>%
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, #id
         srpf_y_ss_ses, #school youth & protective factors: environment
         srpf_y_ss_iiss, #school youth & protective factors: involvement
         srpf_y_ss_dfs, #disengagement from school
         pmq_y_ss_mean, #parental monitoring sum score
         fes_y_ss_fc_pr, #family environment scale: conflict (prorated based on num answered)
         crpbi_y_ss_parent #acceptance subscale of parent completing survey 
  )

abcd_nsc01_n <-   sprintf('%s/abcd_nsc01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_nsc01  <- sprintf('%s/abcd_nsc01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_nsc01_n, na = c('','NA','999','777'), guess_max = 11000) %>%
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, neighborhood_crime_y)

sscey_family <- sscey %>%
  filter(src_subject_id %in% data.family[[1]])

abcd_nsc01_family <- abcd_nsc01 %>%
  filter(src_subject_id %in% data.family[[1]])

```


## Residential Environment

The following measures are derived based on reported addresses. These measures include the Area Deprivation Index, Walkibility Score, Population Density, NO2 and PM25 exposure, Proximity to Roads, and Reported Crimes.

```{r ResidentialVars}


rhds01_n <-   sprintf('%s/abcd_rhds01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
rhds01 <- sprintf('%s/abcd_rhds01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = rhds01_n, na = c('','NA','999','777'), guess_max = 11875) %>%
  filter(eventname=="baseline_year_1_arm_1") 

# log transforming the following variables because they are heavily skewed.
# log1p accounts for 0 values by approximating zeros as a very very small number
rhds01$Res_density_log <- log1p(rhds01$reshist_addr1_d1a) #residential density

rhds01$UCR_GrandTotal_log <- log1p(rhds01$reshist_addr1_grndtot) # grandtotal crime
rhds01$UCR_TotOffenses_log <- log1p(rhds01$reshist_addr1_p1tot) # total adult offenses
rhds01$UCR_ViolCrime_log <- log1p(rhds01$reshist_addr1_p1vlnt) # total adult violent crime
rhds01$UCR_DrugAbuse_log <- log1p(rhds01$reshist_addr1_drugtot) # drug abuse violations
rhds01$UCR_DrugSale_log <- log1p(rhds01$reshist_addr1_drgsale) #drug sale total
rhds01$UCR_DrugPoss_log <- log1p(rhds01$reshist_addr1_drgposs) # drug possession
rhds01$UCR_DUI_log <- log1p(rhds01$reshist_addr1_dui) # dui reports
rhds01$UCR_MJSale_log <- log1p(rhds01$reshist_addr1_mjsale) # marijuana sales

rhds01$ProxRoads_log <- log(rhds01$reshist_addr1_proxrd) # proximity to roads

rhds01$reshist_addr1_adi_ncar_log <- log1p(rhds01$reshist_addr1_adi_ncar)
rhds01$reshist_addr1_adi_ntel_log <- log1p(rhds01$reshist_addr1_adi_ntel)
rhds01$reshist_addr1_adi_nplumb_log <- log1p(rhds01$reshist_addr1_adi_nplumb)
rhds01$reshist_addr1_adi_crowd_log <- log1p(rhds01$reshist_addr1_adi_crowd)

  
```


```{r ResidentialVariablesIncluded, echo=TRUE}
rhds01 <- rhds01 %>%
  select(src_subject_id, #id
         reshist_addr1_adi_perc, #area deprivation index
         reshist_addr1_walkindex, # walkability index
         reshist_addr1_no2, # NO2 levels
         reshist_addr1_pm25, #PM2.5 levels
         ProxRoads_log, # Proximity to roads
         Res_density_log, # residential density
         UCR_GrandTotal_log, UCR_TotOffenses_log, UCR_ViolCrime_log, #crime vars
         UCR_DrugAbuse_log, UCR_DrugSale_log, UCR_DrugPoss_log, UCR_DUI_log, UCR_MJSale_log,
         reshist_addr1_adi_edu_l,
         reshist_addr1_adi_edu_h,
         reshist_addr1_adi_work_c,
         reshist_addr1_adi_income,
         reshist_addr1_adi_in_dis,
         reshist_addr1_adi_home_v,
         reshist_addr1_adi_rent,
         reshist_addr1_adi_mortg,
         reshist_addr1_adi_home_o,
         reshist_addr1_adi_unemp,
         reshist_addr1_adi_pov,
         reshist_addr1_adi_b138,
         reshist_addr1_adi_sp,
         reshist_addr1_adi_ncar_log,
         reshist_addr1_adi_ntel_log, 
         reshist_addr1_adi_nplumb_log, 
         reshist_addr1_adi_crowd_log
) 

rhds01_family <- rhds01 %>%
  filter(src_subject_id %in% data.family[[1]])
```


## Import and summarize cognitive scores

```{r}

mysum  <- function(x)sum(x,na.rm = any(!is.na(x)))
mymean <- function(x)mean(x,na.rm = any(!is.na(x)))

######### Read files #########
NIH_toolbox  <- read.delim(paste(data_dir,"abcd_tbss01.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
Pearson      <- read.delim(paste(data_dir,"abcd_ps01.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
CashChoice   <- read.delim(paste(data_dir,"cct01.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
LittleMan    <- read.delim(paste(data_dir,"lmtp201.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)

Nback        <- read.delim(paste(data_dir,"abcd_mrinback02.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
RecMem       <- read.delim(paste(data_dir,"mribrec02.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
SST          <- read.delim(paste(data_dir,"abcd_sst02.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)
MID          <- read.delim(paste(data_dir,"abcd_mid02.txt",sep=""), na.strings=c(""," ","NA"), stringsAsFactors=FALSE) %>% slice(-1)

######### Retain relevant variables #########
NIH_toolbox  <- unique(subset(NIH_toolbox, select = c(subjectkey, nihtbx_picvocab_uncorrected, nihtbx_flanker_uncorrected, nihtbx_list_uncorrected, 
                                                      nihtbx_cardsort_uncorrected, nihtbx_pattern_uncorrected, nihtbx_picture_uncorrected, nihtbx_reading_uncorrected, 
                                                      nihtbx_fluidcomp_uncorrected, nihtbx_cryst_uncorrected, nihtbx_totalcomp_uncorrected)))

Pearson      <- unique(subset(Pearson, select = c(subjectkey, pea_wiscv_tss, pea_ravlt_sd_trial_i_tc, pea_ravlt_sd_trial_ii_tc, pea_ravlt_sd_trial_iii_tc, 
                                                  pea_ravlt_sd_trial_iv_tc, pea_ravlt_sd_trial_v_tc, pea_ravlt_sd_trial_i_tr, pea_ravlt_sd_trial_ii_tr, 
                                                  pea_ravlt_sd_trial_iii_tr, pea_ravlt_sd_trial_iv_tr, pea_ravlt_sd_trial_v_tr, pea_ravlt_sd_trial_i_ti, 
                                                  pea_ravlt_sd_trial_ii_ti, pea_ravlt_sd_trial_iii_ti, pea_ravlt_sd_trial_iv_ti, pea_ravlt_sd_trial_v_ti, 
                                                  pea_ravlt_sd_listb_tc, pea_ravlt_sd_listb_tr, pea_ravlt_sd_listb_ti, pea_ravlt_sd_trial_vi_tc, pea_ravlt_sd_trial_vi_tr, 
                                                  pea_ravlt_sd_trial_vi_ti, pea_ravlt_ld_trial_vii_tc, pea_ravlt_ld_trial_vii_tr, pea_ravlt_ld_trial_vii_ti)))

CashChoice   <- unique(subset(CashChoice, select = c(subjectkey, cash_choice_task)))

LittleMan    <- unique(subset(LittleMan, select = c(subjectkey, lmt_scr_efficiency, lmt_scr_perc_correct, lmt_scr_rt_correct)))

Nback        <- unique(subset(Nback, select = c(subjectkey, tfmri_nback_beh_switchflag, tfmri_nback_beh_performflag, tfmri_nb_all_beh_ctotal_mrt, 
                                                tfmri_nb_all_beh_ctotal_stdrt, tfmri_nb_all_beh_c0b_rate, tfmri_nb_all_beh_c0bnf_rate, tfmri_nb_all_beh_c0bngf_rate, 
                                                tfmri_nb_all_beh_c0bp_rate, tfmri_nb_all_beh_c0bpf_rate, tfmri_nb_all_beh_c2b_rate, tfmri_nb_all_beh_c2bnf_rate, 
                                                tfmri_nb_all_beh_c2bngf_rate, tfmri_nb_all_beh_c2bp_rate, tfmri_nb_all_beh_c2bpf_rate, tfmri_nb_all_beh_cnf_rate, 
                                                tfmri_nb_all_beh_cngf_rate, tfmri_nb_all_beh_cpf_rate, tfmri_nb_all_beh_cplace_rate, tfmri_nb_all_beh_ctotal_rate)))

RecMem       <- unique(subset(RecMem, select = c(subjectkey, tfmri_rec_beh_switchflag, tfmri_rec_all_beh_posface_br, tfmri_rec_all_beh_posf_dpr, 
                                                 tfmri_rec_all_beh_neutface_br, tfmri_rec_all_beh_neutf_dp, tfmri_rec_all_beh_negface_br, tfmri_rec_all_beh_negf_dp, 
                                                 tfmri_rec_all_beh_place_br, tfmri_rec_all_beh_place_dp)))

SST          <- unique(subset(SST, select = c(subjectkey, tfmri_sst_beh_switchflag, tfmri_sst_beh_performflag, tfmri_sst_all_beh_crgo_rt, tfmri_sst_all_beh_crgo_mrt, 
                                              tfmri_sst_all_beh_crgo_stdrt, tfmri_sst_all_beh_crlg_rt, tfmri_sst_all_beh_incrgo_rt, tfmri_sst_all_beh_incrlg_rt, 
                                              tfmri_sst_all_beh_nrgo_rt, tfmri_sst_all_beh_crs_rt, tfmri_sst_all_beh_incrs_rt, tfmri_sst_all_beh_ssds_rt, 
                                              tfmri_sst_all_beh_tot_mssd, tfmri_sst_all_beh_total_meanrt)))

MID          <- unique(subset(MID, select = c(subjectkey, tfmri_mid_beh_switchflag, tfmri_mid_beh_performflag, tfmri_mid_all_beh_srwpfb_rate, tfmri_mid_all_beh_lrwpfb_rate, 
                                              tfmri_mid_all_beh_slpfb_rate, tfmri_mid_all_beh_llpfb_rate, tfmri_mid_all_beh_ntpfb_rate, tfmri_mid_r1_beh_t_earnings,	
                                              tfmri_mid_r2_beh_t_earnings, tfmri_mid_all_beh_t_earnings)))

######### Convert variables to numeric #########
NIH_toolbox[, 2:ncol(NIH_toolbox)] <- sapply(NIH_toolbox[, 2:ncol(NIH_toolbox)], as.numeric)
Pearson[, 2:ncol(Pearson)]         <- sapply(Pearson[, 2:ncol(Pearson)], as.numeric)
CashChoice[, 2]                    <- sapply(CashChoice[, 2], as.numeric)
LittleMan[, 2:ncol(LittleMan)]     <- sapply(LittleMan[, 2:ncol(LittleMan)], as.numeric)
Nback[, 4:ncol(Nback)]             <- sapply(Nback[, 4:ncol(Nback)], as.numeric)
RecMem[, 3:ncol(RecMem)]           <- sapply(RecMem[, 3:ncol(RecMem)], as.numeric)
SST[, 4:ncol(SST)]                 <- sapply(SST[, 4:ncol(SST)], as.numeric)
MID[, 4:ncol(MID)]                 <- sapply(MID[, 4:ncol(MID)], as.numeric)

######### Add performance measure columns #########
Pearson$pea_ravlt_sd_trial_itov_tc <- apply(Pearson[c('pea_ravlt_sd_trial_i_tc', 'pea_ravlt_sd_trial_ii_tc', 
                                                      'pea_ravlt_sd_trial_iii_tc', 'pea_ravlt_sd_trial_iv_tc', 'pea_ravlt_sd_trial_v_tc')], 1, mysum)

Pearson$pea_ravlt_sd_trial_itov_tr <- apply(Pearson[c('pea_ravlt_sd_trial_i_tr', 'pea_ravlt_sd_trial_ii_tr', 'pea_ravlt_sd_trial_iii_tr', 
                                                      'pea_ravlt_sd_trial_iv_tr', 'pea_ravlt_sd_trial_v_tr')], 1, mysum)

Pearson$pea_ravlt_sd_trial_itov_ti <- apply(Pearson[c('pea_ravlt_sd_trial_i_ti', 'pea_ravlt_sd_trial_ii_ti', 'pea_ravlt_sd_trial_iii_ti', 
                                                      'pea_ravlt_sd_trial_iv_ti', 'pea_ravlt_sd_trial_v_ti')], 1, mysum)

Pearson$pea_ravlt_tc               <- apply(Pearson[c('pea_ravlt_sd_trial_i_tc', 'pea_ravlt_sd_trial_ii_tc', 'pea_ravlt_sd_trial_iii_tc', 
                                                      'pea_ravlt_sd_trial_iv_tc', 'pea_ravlt_sd_trial_v_tc', 'pea_ravlt_sd_listb_tc', 
                                                      'pea_ravlt_sd_trial_vi_tc', 'pea_ravlt_ld_trial_vii_tc')], 1, mysum)

RecMem$overall_dprime              <- apply(RecMem[c('tfmri_rec_all_beh_posf_dpr', 'tfmri_rec_all_beh_neutf_dp', 'tfmri_rec_all_beh_negf_dp', 
                                                     'tfmri_rec_all_beh_place_dp')], 1, mymean)

MID$mean_earnings                  <- apply(MID[c('tfmri_mid_r1_beh_t_earnings', 'tfmri_mid_r2_beh_t_earnings')], 1, mymean)

######### Invert SSRT #########
SST$tfmri_sst_all_beh_total_meanrt <- SST$tfmri_sst_all_beh_total_meanrt*-1

######### Remove cash choice option 3 ("don't know") #########
CashChoice$cash_choice_task[CashChoice$cash_choice_task == 3] <- NA

######### Merge, clean, crop data #########
cog_merge <- Reduce(function(x,y) merge(x = x, y = y, by = "subjectkey", all.x = TRUE, all.y = TRUE), 
                     list(NIH_toolbox, Pearson, 
                          CashChoice, LittleMan, Nback, RecMem, SST, MID))


cog_scores  <- subset(cog_merge, select = c(subjectkey, nihtbx_list_uncorrected, nihtbx_reading_uncorrected, nihtbx_picvocab_uncorrected, 
                                                  tfmri_nb_all_beh_c2b_rate, pea_ravlt_sd_trial_vi_tc, pea_wiscv_tss, pea_ravlt_ld_trial_vii_tc, 
                                                  nihtbx_picture_uncorrected, tfmri_nb_all_beh_c0b_rate, nihtbx_cardsort_uncorrected, nihtbx_flanker_uncorrected, 
                                                  lmt_scr_efficiency, overall_dprime, nihtbx_pattern_uncorrected, mean_earnings, tfmri_sst_all_beh_total_meanrt, 
                                                  cash_choice_task))

colnames(cog_scores)[1] <- "src_subject_id"

cog_scores_family <- cog_scores %>%
  filter(src_subject_id %in% data.family[[1]])

```


## Merging it all together

In this section we merge all of the variables together

```{r mergevariables, echo=TRUE}

all_measures  = list(acspsw03, pdem02, sscep, sscey, abcd_nsc01, rhds01, cog_scores)

compcase1 <- acspsw03[complete.cases(acspsw03),] #11854
compcase2 <- pdem02[complete.cases(pdem02),] #11875
compcase3 <- sscep[complete.cases(sscep),] #11178
compcase4 <- sscey[complete.cases(sscey),] #11834 
compcase5 <- abcd_nsc01[complete.cases(abcd_nsc01),] #11849
compcase6 <- rhds01[complete.cases(rhds01),] #11155
compcase7 <- cog_scores[complete.cases(cog_scores),]

combined_measures <- Reduce(function(dtf1, dtf2) merge(dtf1, dtf2, all.x = TRUE),
                            all_measures)

combined_measures_complete <- combined_measures[complete.cases(combined_measures),]  #9537 

final_subjectlist_allcog <- combined_measures_complete %>%
  select(src_subject_id)
 
write.csv(final_subjectlist_allcog, sprintf('%s/final_subjectlist_allcog.csv', data_dir_subs), row.names = FALSE)
 
```

## Merging all the variables together for the family excluded subset

```{r mergevars_reducedfam}

all_measures_family  = list(acspsw03_family, pdem02_family, sscep_family, sscey_family, 
                            abcd_nsc01_family, rhds01_family, cog_scores_family)

compcase1_family <- acspsw03_family[complete.cases(acspsw03_family),] #9967
compcase2_family <- pdem02_family[complete.cases(pdem02_family),] #9987
compcase3_family <- sscep_family[complete.cases(sscep_family),] #9398
compcase4_family <- sscey_family[complete.cases(sscey_family),] #9949
compcase5_family <- abcd_nsc01_family[complete.cases(abcd_nsc01_family),] #9963
compcase6_family <- rhds01_family[complete.cases(rhds01_family),] #9443
compcase7_family <- cog_scores_family[complete.cases(cog_scores_family),] #

combined_measures_family <- Reduce(function(dtf1, dtf2) merge(dtf1, dtf2, all.x = TRUE),
                            all_measures_family)
combined_measures_complete_family <- combined_measures_family[complete.cases(combined_measures_family),] #8045 

```



##For the overall dataset, we will compute the PCA for the Crime variables, and the MACV variables
```{r CrimePCA, echo=TRUE,results = 'markdown'}

UCRCrime <- combined_measures_complete[c("UCR_GrandTotal_log", "UCR_TotOffenses_log", "UCR_ViolCrime_log", 
                       "UCR_DrugAbuse_log", "UCR_DrugSale_log", "UCR_DrugPoss_log", "UCR_DUI_log",
                       "UCR_MJSale_log")]

res.pca_UCR <- PCA(UCRCrime, scale.unit = TRUE, graph = T) #first PC is 96.8%
fviz_screeplot(res.pca_UCR, addlabels =TRUE)
fviz_pca_var(res.pca_UCR, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
)
fviz_contrib(res.pca_UCR, choice = "var", axes = 1, top = 20)

combined_measures_complete$Crime_PC <- res.pca_UCR$ind$coord[,1]

```

```{r fullcompletecases}

Comb_meas_vars<- combined_measures_complete %>%
  select(interview_age,#demographics
         gender_M,
         race_ethnicity_white,
         race_ethnicity_black,
         race_ethnicity_hispanic, 
         race_ethnicity_asian,
         race_ethnicity_other,
         household.income_num,#SES
         highest.education,
         meim_p_ss_exp,
         meim_p_ss_com,
         macv_p_ss_fo,
         macv_p_ss_fr,
         macv_p_ss_fs,           
         macv_p_ss_isr,           
         macv_p_ss_r,
         fes_p_ss_fc_pr, #home env
         pmq_y_ss_mean,
         fes_y_ss_fc_pr,
         crpbi_y_ss_parent,
         srpf_y_ss_ses,#school env
         srpf_y_ss_iiss,
         srpf_y_ss_dfs,
         nsc_p_ss_mean_3_items, #neighborhood
         neighborhood_crime_y,
         reshist_addr1_walkindex,
         reshist_addr1_no2,
         reshist_addr1_pm25,
         ProxRoads_log,
         Res_density_log,
         UCR_ViolCrime_log, 
         UCR_DrugAbuse_log, 
         UCR_DrugSale_log, 
         UCR_DrugPoss_log, 
         UCR_DUI_log,
         UCR_MJSale_log,
         reshist_addr1_adi_edu_l,
         reshist_addr1_adi_edu_h,
         reshist_addr1_adi_work_c,
         reshist_addr1_adi_income,
         reshist_addr1_adi_in_dis,
         reshist_addr1_adi_home_v,
         reshist_addr1_adi_rent,
         reshist_addr1_adi_mortg,
         reshist_addr1_adi_home_o,
         reshist_addr1_adi_unemp,
         reshist_addr1_adi_pov,
         reshist_addr1_adi_b138,
         reshist_addr1_adi_sp,
         reshist_addr1_adi_ncar_log,
         reshist_addr1_adi_ntel_log, 
         reshist_addr1_adi_nplumb_log, 
         reshist_addr1_adi_crowd_log,
         nihtbx_list_uncorrected,
         nihtbx_picvocab_uncorrected,
         nihtbx_flanker_uncorrected,
         nihtbx_cardsort_uncorrected,
         nihtbx_pattern_uncorrected,
         nihtbx_picture_uncorrected,
         nihtbx_reading_uncorrected,
         pea_wiscv_tss,
         pea_ravlt_sd_trial_vi_tc,
         pea_ravlt_ld_trial_vii_tc,
         lmt_scr_efficiency,
         cash_choice_task,
         tfmri_nb_all_beh_c0b_rate,
         tfmri_nb_all_beh_c2b_rate,
         overall_dprime,
         tfmri_sst_all_beh_total_meanrt,
         mean_earnings  )

colnames(Comb_meas_vars) <- c("Age",
"Male",
"White",
"Black",
"Hispanic",
"Asian",
"Other",
"Income",
"Education",
"EthIdentExploration",
"EthIdentCommitment",
"FamObligation",
"FamReferent",
"FamSupport",
"IndepSelfReliance",
"Religion",
"FamConflict_P",
"ParentMonitoring",
"FamConflict_Y",
"ParentAcceptance",
"SchoolEnvironment",
"SchoolInvolvement",
"SchoolDisengagement",
"NeighSafety_P",
"NeighSafety_Y",
"Walkability",
"NO2Exposure",
"PM25Exposure",
"ProxRoads",
"ResDensity",
"UCR_ViolCrime_log", 
"UCR_DrugAbuse_log", 
"UCR_DrugSale_log", 
"UCR_DrugPoss_log", 
"UCR_DUI_log",
"UCR_MJSale_log",
"ADI_Edu_LTHS",
"ADI_Edu_HSDip",
"ADI_Occ_WhiteCollar",
"ADI_MedianFamInc",
"ADI_IncDisparityIdx",
"ADI_MedianHomeValue",
"ADI_MedianGrossRent",
"ADI_MedianMonthMortg",
"ADI_PercHOwner",
"ADI_PercUnemp",
"ADI_PercFamPoverty",
"ADI_PercPovBelow128",
"ADI_PercSingle",
"ADI_PercLogNCar",
"ADI_PercLogNTel",
"ADI_PercLogNPlumb",
"ADI_PercCrowding",
"NIH_ListSorting_Scores",
"NIH_PicVocab",
"NIH_Flanker",
"NIH_CardSort",
"NIH_PatternComp",
"NIH_PicSeqMem",
"NIH_Reading",
"WISC_Matrix",
"RAVLT_ShortDel",
"RAVLT_LongDel",
"LittleMan",
"CashChoice",
"Neuro_0back",
"Neuro_2back",
"Neuro_EmoRec",
"Neuro_StopSig",
"Neuro_MID")

write.csv(Comb_meas_vars, sprintf('%s/ABCD_EnvVars_allcog.csv',data_dir_subs), row.names = FALSE)

```


Creating variable list and environment type data table

```{r}

CultureVar_list <- data.table(c("EthIdentExploration",
                 "EthIdentCommitment",
                 "FamObligation",
                 "FamReferent",
                 "FamSupport",
                 "IndepSelfReliance",
                 "Religion"), "Culture")

HomeEnvVar_list <- data.table(c("FamConflict_P",
                 "ParentMonitoring",
                 "FamConflict_Y",
                 "ParentAcceptance"), "Home")

SchoolEnvVar_list <- data.table(c("SchoolEnvironment",
                   "SchoolInvolvement",
                   "SchoolDisengagement"), "School")

NeighborhoodEnvVar_list <- data.table(c("NeighSafety_P",
                         "NeighSafety_Y",
                         "Walkability",
                         "NO2Exposure",
                         "PM25Exposure",
                         "ProxRoads",
                         "ResDensity",
                         "UCR_ViolCrime_log", 
                         "UCR_DrugAbuse_log", 
                         "UCR_DrugSale_log", 
                         "UCR_DrugPoss_log", 
                         "UCR_DUI_log",
                         "UCR_MJSale_log",
                         "ADI_Edu_LTHS",
                         "ADI_Edu_HSDip",
                         "ADI_Occ_WhiteCollar",
                         "ADI_MedianFamInc",
                         "ADI_IncDisparityIdx",
                         "ADI_MedianHomeValue",
                         "ADI_MedianGrossRent",
                         "ADI_MedianMonthMortg",
                         "ADI_PercHOwner",
                         "ADI_PercUnemp",
                         "ADI_PercFamPoverty",
                         "ADI_PercPovBelow128",
                         "ADI_PercSingle",
                         "ADI_PercLogNCar",
                         "ADI_PercLogNTel",
                         "ADI_PercLogNPlumb",
                         "ADI_PercCrowding"), "Neighborhood")

combined_envirovar_list <- rbind(CultureVar_list, HomeEnvVar_list, SchoolEnvVar_list, NeighborhoodEnvVar_list)

colnames(combined_envirovar_list) <- c("Variable", "Category")

write_csv(combined_envirovar_list, sprintf('%s/ABCD_EnvVars_combinedlist.csv',data_dir_subs))

```


```{r ReconcileNDAandDEAPNames}

subs_og <- combined_measures_complete$src_subject_id
subs_alternate <- gsub("NDAR_", "sub-NDAR",subs_og)
subs_all <- data.table(subs_orig = subs_og, subs_alt = subs_alternate) ## final number participants = 10288

subs_all_family <- subs_all %>%
  filter(subs_orig %in% data.family[[1]]) ## final number participants = 8701

write.csv(subs_all, sprintf('%s/subs_EnvVars_updated.csv', data_dir_subs), row.names = FALSE)
write.csv(subs_all_family, sprintf('%s/subs_EnvVars_Family_updated.csv', data_dir_subs), row.names = FALSE)

```


```{r PCA All}
res.pca_Combined <- PCA(CombMeasures_resid[,c(1:39)], scale.unit = TRUE, graph = T) #first PC is 96.29%
fviz_screeplot(res.pca_Combined, addlabels =TRUE)
fviz_pca_var(res.pca_Combined, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
)
fviz_contrib(res.pca_Combined, choice = "var", axes = 1, top = 40)

fviz_contrib(res.pca_Combined, choice = "var", axes = 2, top = 40)

summary(res.pca_Combined)
```
```{r PCA_ALL_Family}

res.pca_Combined_Family <- PCA(CombMeasures_family_resid[,c(1:39)], scale.unit = TRUE, graph = T) #first PC is 96.29%
fviz_screeplot(res.pca_Combined_Family, addlabels =TRUE)
fviz_pca_var(res.pca_Combined_Family, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
)
fviz_contrib(res.pca_Combined_Family, choice = "var", axes = 1, top = 20)


```


```{r heatmap}
#install.packages("heatmaply")

library(heatmaply)
my_cor <- cor(CombMeasures_resid)
heatmaply_cor(my_cor)

my_cor_family <- cor(CombMeasures_family_resid)
heatmaply(my_cor_family)
```




